\documentclass[11pt]{article}

\usepackage[a4paper,margin=27mm]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{hyperref}

\hypersetup{
  colorlinks=true,
  linkcolor=blue!50!black,
  citecolor=blue!50!black,
  urlcolor=blue!50!black
}

\setlength{\emergencystretch}{2em}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{remark}[definition]{Remark}
\newtheorem{convention}[definition]{Convention}
\newtheorem{axiom}[definition]{Axiom}
\newtheorem{conjecture}[definition]{Conjecture}

\theoremstyle{plain}
\newtheorem{proposition}[definition]{Proposition}
\newtheorem{theorem}[definition]{Theorem}

\DeclareMathOperator{\supp}{supp}
\DeclareMathOperator{\Read}{Read}
\DeclareMathOperator{\Cl}{Cl}
\DeclareMathOperator{\TopCh}{TopCh}
\DeclareMathOperator{\TopPkg}{TopPkg}
\DeclareMathOperator{\Dow}{Dow}
\DeclareMathOperator{\Contr}{Contr}
\DeclareMathOperator{\Mor}{Mor}
\DeclareMathOperator{\op}{op}
\DeclareMathOperator{\Fis}{Fis}
\DeclareMathOperator{\ClosedResidue}{ClosedResidue}
\DeclareMathOperator{\Buried}{Buried}
\DeclareMathOperator{\RCl}{RCl}
\DeclareMathOperator{\dist}{dist}
\DeclareMathOperator{\skel}{skel}
\DeclareMathOperator{\body}{body}
\DeclareMathOperator{\AxisCl}{AxisCl}
\DeclareMathOperator{\CKMCl}{CKMCl}
\DeclareMathOperator{\Inact}{Inact}
\newcommand{\qu}{\mathrm u}
\newcommand{\qd}{\mathrm d}
\newcommand{\qc}{\mathrm c}
\newcommand{\qs}{\mathrm s}
\newcommand{\qt}{\mathrm t}
\newcommand{\qb}{\mathrm b}

\title{The Grand Meson}
\author{Shuhei Ihara}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
This paper states a precise operational thesis: the Grand Meson is the
update procedure that tests how far the meson concept can be stretched after
the six quark flavors are known, while still recovering the older mesonic
face without discontinuity.  The starting point is the General Meson: a
two-face Yukawa-style mediator read, by convention, through the modern
light pair \(\qu\leftrightarrow\qd\).  Given the external six-flavor
Standard Model input \(F_6\), the Grand Meson completes the two-face object
to a three-axis, six-face skeleton together with a \(36\) oriented
\(q\bar r\)-channel index body.  The extension is
conservative: the
original two-face meson is recovered by projection, while the new faces and
body channels are resolved as open, inactive, or active instead of being
left outside the channel basis.  More precisely, the General Meson is the
substructure of the Grand Meson in which every non-UD face and every non-UD
body channel is buried as a closed inactive residual package.  The observed
three quark generations are represented as internal Grand Meson directions.
Backward compatibility is surjective, but downgrading with unclosed residue
is blocked as a Grand Meson contradiction.  In this paper,
``generalization'' means conservative channel-completion with exact
recovery, not replacement of QCD; ``admissible'' means closed under the
stated mesonic channels; and ``fission'' means a contradictory downgrade
pattern of residual channels, not nuclear fission.  The central claim is
therefore strong but bounded: for the present six-flavor quark sector, the
Grand Meson is an update manual and a continuity test for mesonic elasticity
and robustness.
\end{abstract}

\section{Opening}

A meson is usually approached through its physical role: it mediates an
interaction.  In the present paper the same word is first read through a
paired reconstruction.  In the present reconstruction, the General Meson is
represented by two complementary light-flavor faces.
In the Yukawa-facing reconstruction used here, that channel pair is
\[
  \qu\leftrightarrow\qd.
\]
This is not a quark--quark bound state.  It is the light-flavor channel face
from which the QCD readout later forms \(q\bar r\) channels such as
\(\qu\bar{\qd}\), \(\qd\bar{\qu}\), \(\qu\bar{\qu}\), and
\(\qd\bar{\qd}\).  Yukawa did not formulate his meson with quark flavors;
the notation is the modern light-flavor pair through which this paper
rereads the proton--neutron mediation problem.

The former working nickname ``Ethon'' is retired here.  The technical
object of this paper is the Grand Meson.  The name is structural, not
honorific: ``grand'' means that, after the six-flavor Standard Model input
is supplied, a two-face light-pair reconstruction is embedded into the
admissible three-axis bookkeeping case.

\begin{convention}[Yukawa-facing reconstruction]
The implication
\[
  \text{Yukawa mediator}\quad\leadsto\quad
  A_Y=\{\qu,\qd\}
\]
is not a historical or physical derivation.  It is the convention used in
this paper: the Yukawa mediator problem is read through the modern light
flavor pair \(\qu,\qd\).  All claims about the General Meson begin only
after this reconstruction has been fixed.
\end{convention}

\section{Operational Thesis}

The Grand Meson is not introduced as a new bound state and not as a
replacement for the standard quark--antiquark meson.  It is introduced as a
channel-completion operation on the mesonic flavor sector.  Its purpose is
to make the following claim explicit:
\[
  \text{mesonic elasticity}
  =
  \text{extension to six flavor faces without loss of recovery}.
\]
The corresponding robustness condition is exact projection back to the
older face:
\[
\begin{aligned}
  \text{mesonic robustness}
  ={}&
  \bigl(p^{\mathrm{raw}}_{\qu\qd}(g)=m\bigr)
  \\
  &{}\wedge
  \ClosedResidue^{\mathrm{face}}_{d}
  \bigl(R^{\mathrm{face}}_{\perp}(g)\bigr)
  \\
  &{}\wedge
  \ClosedResidue^{\mathrm{body}}_{U}
  \bigl(R^{\mathrm{body}}_{\perp}(G)\bigr).
\end{aligned}
\]
Thus the paper is an update manual for mesonic channel operations and a
verification of operational continuity.  A Grand Meson statement is
well formed only when the older General Meson face is recovered and every
residual channel is closed.

\begin{remark}[Historical status]
The pair \(\qu\leftrightarrow\qd\) is not claimed to be Yukawa's original
notation.  It is a modern light-flavor reconstruction of the mediation
problem that Yukawa isolated.  The historical input is the mediator problem;
the Grand Meson construction is the present six-flavor completion procedure.
\end{remark}

\section{Standard Mesonic Channel Data}

Let the six known quark flavors be
\[
  F_6=\{\qu,\qd,\qc,\qs,\qt,\qb\}.
\]

\begin{convention}[Six-flavor input]
The passage from the General Meson to the Grand Meson is not an internal
theorem of the two-face object.  It is the completion problem obtained
after the six known quark flavors \(F_6\) are supplied as external Standard
Model input:
\[
  \mathsf{Grand}
  =
  \mathrm{Completion}_{F_6}(\mathsf{Gen}).
\]
The symbol \(\mathrm{Completion}_{F_6}\) is only announced here; it is
defined below by the body zero extension
\(z^{\mathrm{body}}\), the missing-channel completion
\(\mathcal C_{\mathrm{GM}}\), and the skeleton map \(\skel\).
Thus the additional \(\qc,\qs,\qt,\qb\) directions are not inferred from
the Yukawa-facing face alone; they are admitted because the target channel
basis is the present six-flavor mesonic sector.
\end{convention}

The physical body of a mesonic channel is not a single flavor face but an
oriented quark--antiquark channel
\[
  (q,\bar r)\in F_6\times \overline{F_6}.
\]
For a spin-parity sector \(\sigma\), let \(\Gamma_\sigma\) be the
corresponding Dirac structure and define the standard color-singlet
interpolating bilinear
\[
  O^{\Gamma_\sigma}_{q\bar r}(x)
  :=
  \sum_{a=1}^{3}\bar r_a(x)\Gamma_\sigma q^a(x).
\]
When the spin-parity sector is fixed or irrelevant to the displayed
formula, write \(O_{q\bar r}\) for \(O^{\Gamma_\sigma}_{q\bar r}\).
Let \(Q_q\) be the electric charge of \(q\), and let
\(e_q\in\mathbb Z^{F_6}\) be the flavor unit at \(q\).  For a spin-parity
sector \(\sigma\), define the QCD quantum fingerprint
\[
  \nu_{\mathrm{QCD}}(q,\bar r;\sigma)
  :=
  (\sigma,\ Q_q-Q_r,\ e_q-e_r,\ \mathsf B_{\mathrm{ary}}=0,\
  \mathbf 1_{\mathrm c}).
\]
Here \(\mathsf B_{\mathrm{ary}}\) denotes baryon number and is not the
bottom-flavor label \(\qb\).

\begin{definition}[Mesonic polymer package]
For \(q,r\in F_6\), a mesonic polymer is the channel package
\[
  P_{q\bar r}
  :=
  (O^{\Gamma_\sigma}_{q\bar r},\ J^{q\bar r}_{\sigma},\
    \nu_{\mathrm{QCD}}(q,\bar r;\sigma),\
    C_{q\bar r,\bullet},\
    K_{\mathrm{QCD}}(q\bar r)).
\]
Here \(J^{q\bar r}_{\sigma}\) is the source coefficient for the
Dirac/spin-parity sector,
\(C_{q\bar r,\bullet}\) denotes the corresponding correlator family, and
\(K_{\mathrm{QCD}}\) denotes the ordinary QCD conservation data.  Set
\[
  \mathsf{PrePol}_{q\bar r}
  :=
  \{\,P_{q\bar r}\mid
  P_{q\bar r}\ \text{is a well-typed package of the displayed form}\,\}.
\]
\[
  \mathsf{PrePol}
  :=
  \bigsqcup_{q,r\in F_6}\mathsf{PrePol}_{q\bar r}.
\]
\[
  \mathsf{Pol}_{q\bar r}
  :=
  \{\,P\in\mathsf{PrePol}_{q\bar r}\mid
    \Cl(P)=\Cl_{\mathrm{GM}}\,\}.
\]
\[
  \mathsf{Pol}
  :=
  \bigsqcup_{q,r\in F_6}\mathsf{Pol}_{q\bar r}.
\]
Thus \(\mathsf{PrePol}\) is the inspection space and \(\mathsf{Pol}\) is
the closed subspace.  The closure predicates below may be evaluated on
\(\mathsf{PrePol}\); only packages passing them inhabit \(\mathsf{Pol}\).
\end{definition}

\begin{definition}[Grand Meson closure suite]
Let
\[
\begin{aligned}
  \Cl_{\mathrm{QCD}}
  &:=
  \{\mathrm{Color}_1,\mathrm{Lorentz},\mathrm{Charge},
    \mathrm{Flavor}\},
  \\
  \Cl_{\mathrm{weak}}
  &:=
  \{\mathrm{CKMCl},\mathrm{TopPkg}\},
  \\
  \Cl_{\mathrm{readout}}
  &:=
  \{\mathrm{Threshold},\mathrm{Observable}\}.
\end{aligned}
\]
The Grand Meson closure suite is the layered union
\[
  \Cl_{\mathrm{GM}}
  :=
  \Cl_{\mathrm{QCD}}\cup\Cl_{\mathrm{weak}}\cup\Cl_{\mathrm{readout}}.
\]
For a channel package \(P\), \(\Cl(P)\subseteq\Cl_{\mathrm{GM}}\) is the
set of closure tests satisfied by \(P\).  A package is Grand-closed when
\[
  \Cl(P)=\Cl_{\mathrm{GM}}.
\]
The entries of \(\Cl_{\mathrm{GM}}\) are predicates on a package:
\[
  \begin{gathered}
  \mathrm{Color}_1(P),\ \mathrm{Lorentz}(P),\
  \mathrm{Charge}(P),\ \mathrm{Flavor}(P),\\
  \CKMCl(P),\ \TopPkg(P),\
  \mathrm{Threshold}(P),\ \mathrm{Observable}(P).
  \end{gathered}
\]
For residual closure we use typed predicates rather than one untyped set:
\[
  \RCl_{\mathrm{face}}(d)\subseteq F_6,\qquad
  \RCl_{\mathrm{body}}(U)\subseteq F_6\times\overline{F_6}.
\]
Let \(\mathsf{ClosureObjects}\) be the typed disjoint union of closure
witnesses used in this paper: QCD closure witnesses, weak-current closure
witnesses, top-exit witnesses, threshold witnesses, observable-readout
witnesses, and residual-closure records.
The channel residual-closure assignment type is
\[
  \mathsf{ChResType}
  :=
  \left\{
  \mathcal R_{\mathrm{ch}}
  \ \middle|\
  \mathcal R_{\mathrm{ch}}(q\bar r)\subseteq\mathsf{ClosureObjects}
  \text{ for all }q,r\in F_6
  \right\}.
\]
Here \(d\) is a face downgrade symbol and \(U\) is a body transition
symbol.  Thus \(\Cl(P)\) is a test-suite value of a package, while
\(\RCl_{\mathrm{face}}\), \(\RCl_{\mathrm{body}}\), and
\(\mathsf{ChResType}\) are residual-closure data of different types.
The QCD layer contains color singletness, Lorentz covariance,
electric-charge conservation, and flavor bookkeeping.  The weak layer
contains charged-current CKM closure and top-axis weak-virtual closure.
The readout layer contains threshold or decay closure and observable
readout.  The paper never treats CKM closure as a color-QCD closure; it is
an additional weak-current closure condition carried by the Grand Meson
package.
The weak predicates are conditional predicates:
\[
  \CKMCl(P)
  \quad\text{is vacuous unless }P\text{ uses a weak charged current,}
\]
and
\[
  \TopPkg(P_{q\bar r})
  \quad\text{is vacuous unless }q=\qt\text{ or }r=\qt.
\]
For a top-bearing package, \(\TopPkg(P_{q\bar r})\) is satisfied only
when the weak-virtual top-exit closure defined below is supplied.
\end{definition}

\begin{definition}[Typed Grand Meson contradiction]
A Grand Meson contradiction is not a contradiction of QCD.  It is the
impossibility of inhabiting the declared Grand Meson readout or transition
space.  We use the typed family
\[
  \Contr_{\mathrm{dow}}(d),\qquad
  \Contr_{\mathrm{top}}(P_{q\bar r};\mathcal R_{\mathrm{ch}}),\qquad
  \Contr_{\bar F}(O_{q\bar r}\equiv O_{s\bar t}),\qquad
  \Contr_{\mathrm{tr}}(U).
\]
The shorthand \(\Contr_{\mathrm{GM}}\) refers to this disjoint family only
when the input type is clear from context.
\end{definition}

\begin{definition}[Inactive residual package]
Let
\[
  \mathsf{Prov}_{0}
  :=
  \{\mathrm{selection},\mathrm{kinematic},\mathrm{coupling},
    \mathrm{sensitivity},\mathrm{integrated},\mathrm{buried},
    \mathrm{fuse}\}.
\]
For each oriented channel \(q\bar r\), define a closed inactive package
\[
  \mathbf 0_{q\bar r}[\rho],
  \qquad
  \rho\in\mathsf{Prov}_{0}.
\]
It is typed by the channel \(q\bar r\), carries zero source and zero
ordinary readout contribution, and satisfies the Grand Meson closure suite
as an inactive residual package:
\[
  \Cl(\mathbf 0_{q\bar r}[\rho])=\Cl_{\mathrm{GM}}.
\]
Set
\[
  \mathsf{Pol}^{\mathrm{res}}_{q\bar r}
  :=
  \mathsf{Pol}_{q\bar r}\cup
  \{\,\mathbf 0_{q\bar r}[\rho]
  \mid
  \rho\in\mathsf{Prov}_{0}\,\},
  \qquad
  \mathsf{Pol}^{\mathrm{res}}
  :=
  \bigsqcup_{q,r\in F_6}\mathsf{Pol}^{\mathrm{res}}_{q\bar r}.
\]
The corresponding pre-closure residual type is
\[
  \mathsf{PrePol}^{\mathrm{res}}_{q\bar r}
  :=
  \mathsf{PrePol}_{q\bar r}\cup
  \{\,\mathbf 0_{q\bar r}[\rho]
  \mid
  \rho\in\mathsf{Prov}_{0}\,\}.
\]
\end{definition}

\begin{definition}[Face package]
A flavor face is not itself an oriented mesonic channel.  It is the full
family of oriented channels incident to that face relative to a chosen
flavor domain \(S\subseteq F_6\):
\[
  \mathsf{Face}^{\mathrm{res}}_{q|S}
  :=
  \prod_{r\in S}\mathsf{PrePol}^{\mathrm{res}}_{q\bar r}
  \times
  \prod_{s\in S}\mathsf{PrePol}^{\mathrm{res}}_{s\bar q}.
\]
Write \(\mathsf{Face}^{\mathrm{res}}_{q}:=
\mathsf{Face}^{\mathrm{res}}_{q|F_6}\) for the full Grand Meson face.
The closed inactive face package is therefore
\[
  \mathbf 0_{q|S}[\rho]
  :=
  \left(
    (\mathbf 0_{q\bar r}[\rho])_{r\in S},\
    (\mathbf 0_{s\bar q}[\rho])_{s\in S}
  \right)
  \in \mathsf{Face}^{\mathrm{res}}_{q|S}.
\]
Write \(\mathbf 0_q[\rho]:=\mathbf 0_{q|F_6}[\rho]\).
Set
\[
  \mathsf{Face}^{\mathrm{res}}
  :=
  \prod_{q\in F_6}\mathsf{Face}^{\mathrm{res}}_q .
\]
\end{definition}

\section{The General Meson}

Let the Yukawa-facing readable pair be
\[
  A_Y=\{\qu,\qd\}.
\]
The smallest face-level implementation may be generated from
\[
  \mathbb P_3=\{\mathbf{-1},\mathbf 0,\mathbf{+1}\},
\]
but no physical charge, amplitude, or particle identity is assigned to
these pseudo-values before a \(q\bar r\)-channel package is supplied.

\begin{remark}[Role of \(\mathsf{Pol}\)]
\(\mathsf{Pol}\) denotes the active closed mesonic package space above, and
\(\mathsf{Pol}^{\mathrm{res}}\) adds closed inactive residual packages.
Containers such as faces and bodies use \(\mathsf{PrePol}^{\mathrm{res}}\)
so that closure tests can still reject an open active package at readout
time.
The six-face notation is therefore a skeleton notation built from
\(\mathsf{Face}^{\mathrm{res}}_q\).  The physical mesonic body lives over
\(F_6\times\overline{F_6}\).
\end{remark}

\begin{definition}[General Meson]
A raw General Meson is a two-face mesonic skeleton
\[
  m\in
  \mathsf{Gen}^{\mathrm{raw}}
  :=
  \prod_{q\in A_Y}\mathsf{Face}^{\mathrm{res}}_{q|A_Y}.
\]
Its inspectable oriented UD body is
\[
  \mathsf{PreBody}_{Y}
  :=
  \prod_{q,r\in A_Y}\mathsf{PrePol}^{\mathrm{res}}_{q\bar r}.
\]
Its closed oriented UD body is
\[
  \mathsf{Body}_{Y}^{\mathrm{cl}}
  :=
  \{\,M\in\mathsf{PreBody}_{Y}\mid
  \Inact(M(q,\bar r))\ \text{or}\
  \Cl(M(q,\bar r))=\Cl_{\mathrm{GM}}
  \text{ for all }q,r\in A_Y\,\}.
\]
Define the UD skeleton map
\[
  \skel_Y:\mathsf{PreBody}_{Y}\longrightarrow\mathsf{Gen}^{\mathrm{raw}}
\]
by
\[
  \skel_Y(M)(q)
  :=
  \left(
    (M(q,\bar r))_{r\in A_Y},\
    (M(s,\bar q))_{s\in A_Y}
  \right).
\]
The glued General Meson is
\[
  \mathsf{Gen}_{\mathrm{comp}}
  :=
  \operatorname{Im}
  \bigl(\skel_Y:\mathsf{Body}_{Y}^{\mathrm{cl}}
  \to\mathsf{Gen}^{\mathrm{raw}}\bigr)
  \subseteq
  \mathsf{Gen}^{\mathrm{raw}}.
\]
The map \(\skel_Y\) is injective, since each \(M(q,\bar r)\) occurs in
the outgoing family of the \(q\)-face.  Hence a glued General Meson has a
unique body, denoted \(\body_Y(m)\).  From this point onward, unqualified
\(\mathsf{Gen}\) means \(\mathsf{Gen}_{\mathrm{comp}}\).
The faces \(\qu\) and \(\qd\) are the two light-flavor faces of the
Yukawa-style mesonic channel.  They are face packages, not two constituents
of a physical meson.  The physical body supplied by those faces is the four
oriented UD channels
\[
  \qu\bar{\qu},\quad \qu\bar{\qd},\quad
  \qd\bar{\qu},\quad \qd\bar{\qd}.
\]
\end{definition}

This definition deliberately keeps the Yukawa-style mediator idea narrow.
It does not say that a meson is universal.  It says only that the basic
mesonic act is readable mediation across the \(\qu,\qd\) light pair.  In
that restricted sense, the General Meson is a deliberately narrow readout
for the nuclear-force problem: the proton--neutron transition axis is
specified by the reconstruction convention.
The light-pair configuration is not by itself a derivation of the Yukawa
potential.  That recovery belongs to the low-energy pion channel after the
QCD readout has supplied \(q\bar r\) operators, quantum numbers, and
observables.

\section{The Hidden Cost of Missing Channels}

The decisive distinction is between an inactive channel and a missing
channel.  An inactive channel belongs to the channel basis and carries no
active contribution.  A missing channel has not entered the channel basis.

\[
  \mathbf 0=\text{resolved inactive channel},
  \qquad
  \bot_{q\bar r}=\text{missing oriented channel},
  \qquad
  \bot_q=\text{missing face}.
\]

\begin{definition}[Inactive-channel provenance]
The symbol \(\mathbf 0\) is a formal null, not a universal physical zero.
When physical input is available, an inactive channel may be refined by a
provenance tag
\[
  \mathbf 0[\rho],
  \qquad
  \rho\in
  \{\mathrm{selection},\mathrm{kinematic},\mathrm{coupling},
    \mathrm{sensitivity},\mathrm{integrated}\}.
\]
Thus a selection-blocked channel, an energetically unreachable channel, a zero
coupling, an experimentally unresolved signal, and an integrated-out
contribution are not collapsed into the same physical claim.
\end{definition}

\begin{definition}[Missing-channel lift]
The missing-channel lift of a General Meson \(m\in\mathsf{Gen}\) is
\[
  L_{\bot}(m)\in
  \prod_{q\in F_6}\mathsf{Face}^{\bot}_{q|F_6},
\]
where
\[
  \mathsf{Face}^{\bot}_{q|S}
  :=
  \prod_{r\in S}
    \bigl(\mathsf{PrePol}^{\mathrm{res}}_{q\bar r}\cup\{\bot_{q\bar r}\}\bigr)
  \times
  \prod_{s\in S}
    \bigl(\mathsf{PrePol}^{\mathrm{res}}_{s\bar q}\cup\{\bot_{s\bar q}\}\bigr).
\]
For \(q\in A_Y\), \(L_{\bot}(m)(q)\) agrees with \(m(q)\) on the incident
UD slots and assigns the appropriate missing symbols to every incident
slot whose other endpoint lies outside \(A_Y\).  For \(q\notin A_Y\), every
incident slot of \(L_{\bot}(m)(q)\) is missing; this face is written
\(\bot_{q|F_6}\).
\end{definition}

\begin{definition}[Componentwise missing-channel completion]
Missing channels do not become inactive by inference.  They become inactive
only by the Grand completion operator
\[
  \mathcal C_{\mathrm{GM}}.
\]
On an already supplied oriented package, it is the identity:
\[
  \mathcal C_{\mathrm{GM}}(P)=P
  \qquad
  (P\in\mathsf{PrePol}^{\mathrm{res}}_{q\bar r}).
\]
On an oriented missing channel it is defined by
\[
  \mathcal C_{\mathrm{GM}}(\bot_{q\bar r})
  :=
  \mathbf 0_{q\bar r}[\mathrm{buried}],
\]
and on a missing face carrying its relative domain \(S\subseteq F_6\), by
\[
  \mathcal C_{\mathrm{GM}}(\bot_{q|S})
  :=
  \mathbf 0_{q|S}[\mathrm{buried}].
\]
The operator extends componentwise to partial face skeletons and partial
body skeletons: it fixes every supplied package and sends every missing
entry to the corresponding buried inactive package.  Therefore
\(\mathcal C_{\mathrm{GM}}(L_{\bot}(m))\) means componentwise completion of
all missing entries of \(L_{\bot}(m)\) while leaving the already supplied
UD data unchanged.
Thus
\[
  \bot_{q\bar r}
  \not\equiv
  \mathbf 0_{q\bar r}[\mathrm{buried}],
  \qquad
  \mathcal C_{\mathrm{GM}}(\bot_{q\bar r})
  =
  \mathbf 0_{q\bar r}[\mathrm{buried}].
\]
The first formula preserves the distinction between absent and inactive;
the second formula names the completion rule that upgrades an absent
channel into a present, closed, inactive residual package.
\end{definition}

Thus the remaining axes are not false, not zero, and not disproved.  They
are absent from the original face basis.  The two-face theory remains
locally correct while it cannot close propagation that travels
through the missing directions.

\begin{remark}[Physical reading]
The missing faces are not a defect in the original General Meson.  They
are the price of a successful restriction.  A narrow mediator may solve its
local problem precisely because it does not carry the full burden of every
other axis.
\end{remark}

\section{The Grand Meson Face Skeleton}

Given the external six-flavor Standard Model input \(F_6\), the first layer
of the Grand Meson is obtained by completing missing flavor faces into
resolved flavor faces.  This is the raw face skeleton.  It is not yet the
full mesonic operator body; physical mesons enter through the oriented
\(q\bar r\)-channel completion defined later.

\begin{definition}[Grand Meson face skeleton]
A Grand Meson first appears as a raw six-face mesonic skeleton
\[
  g\in\mathsf{Grand}^{\mathrm{raw}}
  :=
  \prod_{q\in F_6}\mathsf{Face}^{\mathrm{res}}_q .
\]
This raw product is larger than the body-compatible Grand Meson defined
later: it has not yet imposed that the same \(q\bar r\) package agrees when
read from the \(q\)-face and from the \(r\)-face.
The six faces are grouped into three readable axes:
\[
  \qu\leftrightarrow\qd,\qquad
  \qc\leftrightarrow\qs,\qquad
  \qt\leftrightarrow\qb.
\]
These axes are internal flavor-generation axes.  They are not spatial
directions, and they are not quark--quark bound states.  Physical mesons
enter through oriented \(q\bar r\) channels in the QCD readout.
\end{definition}

In this notation the Grand Meson is the admissible \(n=3\) object:
\[
  \mathsf{Grand}^{\mathrm{raw}}
  =
  \prod_{q\in F_6}\mathsf{Face}^{\mathrm{res}}_q
  \qquad(n=3).
\]
The adjective ``admissible'' means that all three axes belong to the
channel basis after the external six-flavor input has been supplied.  It
does not mean that every transition is allowed, nor that every physical
theory has been solved.

\begin{definition}[Channel support]
For an oriented package, write
\[
  \Inact(P_{q\bar r})
  \quad\Longleftrightarrow\quad
  P_{q\bar r}=\mathbf 0_{q\bar r}[\rho]
  \text{ for some }\rho\in\mathsf{Prov}_{0}.
\]
Also write
\[
  \Buried(P_{q\bar r})
  \quad\Longleftrightarrow\quad
  P_{q\bar r}=\mathbf 0_{q\bar r}[\mathrm{buried}].
\]
For a face package \(f_q\in\mathsf{Face}^{\mathrm{res}}_q\), write
\(\Inact(f_q)\) when every incident oriented component of \(f_q\) is
inactive, allowing different provenance tags on different incident
channels.  The predicate is overloaded on face packages by
\[
  \Buried(f_q)
  \quad\Longleftrightarrow\quad
  \text{every incident component of }f_q
  \text{ is }\mathbf 0[\mathrm{buried}]
  \text{ in its own channel type}.
\]
For \(g\in\mathsf{Grand}^{\mathrm{raw}}\), define the face support by
\[
  \supp_{\mathrm{face}}(g)
  =
  \{q\in F_6\mid \neg\Inact(g(q))\}.
\]
A Grand Meson may have inactive channels, but inactivity is resolved by
channelwise residual packages, not by \(\bot\).
\end{definition}

\section{Conservative Recovery}

The Grand Meson must not destroy the General Meson.  It must contain it as
the two-channel face that was already working.

\begin{definition}[Raw projection to the General Meson]
Define the raw \(\qu,\qd\)-projection
\[
  p^{\mathrm{raw}}_{\qu\qd}:
  \mathsf{Grand}^{\mathrm{raw}}\to\mathsf{Gen}^{\mathrm{raw}}
\]
by
\[
  p^{\mathrm{raw}}_{\qu\qd}(g)(q)=g(q)|_{A_Y}
  \quad(q\in A_Y),
\]
where \(g(q)|_{A_Y}\) forgets every incident channel outside
\(A_Y\times\overline{A_Y}\).
\end{definition}

\begin{proposition}[Conservative recovery]
Every raw General Meson is recovered from any raw Grand Meson whose restricted
\(\qu,\qd\)-faces agree with it.  In particular, if
\(g(q)|_{A_Y}=m(q)\) for \(q\in A_Y\), then
\[
  p^{\mathrm{raw}}_{\qu\qd}(g)=m.
\]
\end{proposition}

\begin{proof}
The restriction \(p^{\mathrm{raw}}_{\qu\qd}\) reads exactly the two
light-face packages.
Therefore agreement on those two faces is sufficient and necessary for the
stated projection recovery.
\end{proof}

This is the main discipline of the construction.  The Grand Meson does not
rewrite the older meson.  It keeps the working \(\qu\leftrightarrow\qd\)
face and opens two additional quark-pair faces under explicit channel
closure.

\section{Surjective Backward Compatibility}

Backward compatibility must be surjective, not merely suggestive.  Every
General Meson must be obtainable as the visible face of at least one Grand
Meson.

\begin{definition}[Zero extension]
For \(m\in\mathsf{Gen}^{\mathrm{raw}}\), define the raw zero extension
\[
  z^{\mathrm{raw}}(m)\in\mathsf{Grand}^{\mathrm{raw}}
\]
as follows.  For \(q\in A_Y\), let \(\widehat m_q\in
\mathsf{Face}^{\mathrm{res}}_q\) be the full-face extension that agrees
with \(m(q)\) on the incident UD channels and assigns
\(\mathbf 0_{a\bar b}[\mathrm{buried}]\) to every incident channel
outside \(A_Y\times\overline{A_Y}\).  Then
\[
  z^{\mathrm{raw}}(m)(\qu)=\widehat m_{\qu},\qquad
  z^{\mathrm{raw}}(m)(\qd)=\widehat m_{\qd},
\]
and
\[
  z^{\mathrm{raw}}(m)(q)=\mathbf 0_q[\mathrm{buried}]
  \qquad(q\in F_6\setminus A_Y).
\]
\end{definition}

\begin{proposition}[Surjective backward map]
The projection
\(p^{\mathrm{raw}}_{\qu\qd}:\mathsf{Grand}^{\mathrm{raw}}\to
\mathsf{Gen}^{\mathrm{raw}}\) satisfies
surjective:
\[
  p^{\mathrm{raw}}_{\qu\qd}\circ z^{\mathrm{raw}}
  =\mathrm{id}_{\mathsf{Gen}^{\mathrm{raw}}}.
\]
\end{proposition}

\begin{proof}
The zero extension preserves the \(\qu,\qd\)-face of \(m\) and resolves
all other channels as inactive.  Projecting back to the
\(\qu,\qd\)-face therefore returns exactly \(m\).
\end{proof}

\begin{definition}[UD burial normalization]
Define the UD-burial subobject
\[
  \mathsf{Grand}_{\qu\qd}^{0}
  :=
  z^{\mathrm{raw}}(\mathsf{Gen}^{\mathrm{raw}})
  =
  \{\,z^{\mathrm{raw}}(m)\mid m\in\mathsf{Gen}^{\mathrm{raw}}\,\}.
\]
The burial normalization
\[
  \beta_{\qu\qd}:\mathsf{Grand}^{\mathrm{raw}}\longrightarrow
  \mathsf{Grand}_{\qu\qd}^{0}
\]
is defined by
\[
  \beta_{\qu\qd}(g):=
  z^{\mathrm{raw}}(p^{\mathrm{raw}}_{\qu\qd}(g)).
\]
Here \(\mathbf 0_q[\mathrm{buried}]\) is a closed inactive residual package,
not a deletion and not an absent channel.  Other provenance tags describe
other inactive mechanisms, but the canonical recovery of \(\mathsf{Gen}\)
uses the buried tag.
\end{definition}

\begin{proposition}[General Meson as buried Grand Meson]
Restriction to the UD face gives an isomorphism
\[
  \mathsf{Grand}_{\qu\qd}^{0}\cong\mathsf{Gen}^{\mathrm{raw}}.
\]
More explicitly,
\[
  p^{\mathrm{raw}}_{\qu\qd}|_{\mathsf{Grand}_{\qu\qd}^{0}}
  :\mathsf{Grand}_{\qu\qd}^{0}\to\mathsf{Gen}^{\mathrm{raw}}
\]
has inverse
\(z^{\mathrm{raw}}:\mathsf{Gen}^{\mathrm{raw}}\to
\mathsf{Grand}_{\qu\qd}^{0}\).
\end{proposition}

\begin{proof}
By definition, every \(h\in\mathsf{Grand}_{\qu\qd}^{0}\) has the form
\(h=z^{\mathrm{raw}}(m)\) for a unique
\(m\in\mathsf{Gen}^{\mathrm{raw}}\).  Conversely, \(z^{\mathrm{raw}}(m)\)
preserves the UD-restricted face data of \(m\) and fills every incident
non-UD channel with a closed inactive package.  Hence
\[
  p^{\mathrm{raw}}_{\qu\qd}\circ z^{\mathrm{raw}}
  =\mathrm{id}_{\mathsf{Gen}^{\mathrm{raw}}},
  \qquad
  z^{\mathrm{raw}}\circ p^{\mathrm{raw}}_{\qu\qd}
  =
  \mathrm{id}_{\mathsf{Grand}_{\qu\qd}^{0}}.
\]
\end{proof}

Surjectivity gives power: a Grand Meson can always be normalized to an
ordinary General Meson by burying the non-UD faces as closed inactive
packages.  The same operation also carries responsibility, because active
non-UD structure must be closed as residue rather than ignored.

\begin{axiom}[Grand Meson downgrade admissibility]
Recoverability is not the same as downgrade admissibility:
\[
  p^{\mathrm{raw}}_{\qu\qd}(g)=m
  \not\Rightarrow
  d\in\Dow_{\mathrm{GM}}(g,m).
\]
A proposed downgrade \(d:g\Downarrow m\) is admissible only when it both
recovers the General Meson face and supplies closed residual witnesses for
the non-UD data:
\[
  d\in\Dow_{\mathrm{GM}}(g,m)
  \quad\Longleftrightarrow\quad
  p^{\mathrm{raw}}_{\qu\qd}(g)=m
  \ \text{and}\
  \ClosedResidue^{\mathrm{face}}_{d}
  (R^{\mathrm{face}}_{\perp}(g)).
\]
Thus residue responsibility is an explicit Grand Meson admissibility rule,
not a theorem following from
\(p^{\mathrm{raw}}_{\qu\qd}\circ z^{\mathrm{raw}}=\mathrm{id}\).
\end{axiom}

\begin{definition}[Downgrade residue and closure]
For \(g\in\mathsf{Grand}^{\mathrm{raw}}\), define the downgrade residue
\[
  R^{\mathrm{face}}_{\perp}(g):=g|_{F_6\setminus A_Y}
\]
and its non-buried residue support
\[
  S^{\mathrm{face}}_{\perp}(g)
  :=
  \{\,q\in F_6\setminus A_Y\mid
  \neg\Buried(g(q))\,\}.
\]
For a proposed downgrade symbol \(d:g\Downarrow m\), the predicate
\[
  \ClosedResidue^{\mathrm{face}}_d(R^{\mathrm{face}}_{\perp}(g))
\]
means that \(d\) carries a residual witness
\[
  \chi_d:S^{\mathrm{face}}_{\perp}(g)\longrightarrow
  \RCl_{\mathrm{face}}(d)
\]
and that every face in \(S^{\mathrm{face}}_{\perp}(g)\) is sent by the
normalization to the closed inactive family
\(\mathbf 0_q[\mathrm{buried}]\).  Projection alone is therefore not a
downgrade; projection plus residual witness is.
For a proposed downgrade symbol \(d:g\Downarrow m\), define the Grand
Meson downgrade class
\[
  \Dow_{\mathrm{GM}}(g,m)
  :=
  \{\,d:g\Downarrow m
  \mid
  p^{\mathrm{raw}}_{\qu\qd}(g)=m
  \ \mathrm{and}\
  \ClosedResidue^{\mathrm{face}}_d(R^{\mathrm{face}}_{\perp}(g))\,\}.
\]
The contradiction predicate is
\[
  \Contr_{\mathrm{dow}}(d)
  :=
  \bigl(p^{\mathrm{raw}}_{\qu\qd}(s(d))=t(d)\bigr)
  \wedge
  \bigl(S^{\mathrm{face}}_{\perp}(s(d))\ne\varnothing\bigr)
  \wedge
  \neg\ClosedResidue^{\mathrm{face}}_d(R^{\mathrm{face}}_{\perp}(s(d))).
\]
Here \(s(d)=g\) and \(t(d)=m\) are the source and target carried by the
typed downgrade symbol \(d:g\Downarrow m\).
\end{definition}

\begin{proposition}[Robust downgrade block]
If \(\Contr_{\mathrm{dow}}(d)\) holds for a proposed downgrade symbol
\(d:g\Downarrow m\), then
\[
  d\notin\Dow_{\mathrm{GM}}(g,m).
\]
If every proposed downgrade symbol from \(g\) to \(m\) is contradictory, then
\[
  \Dow_{\mathrm{GM}}(g,m)=\varnothing .
\]
\end{proposition}

\begin{proof}
Membership in \(\Dow_{\mathrm{GM}}(g,m)\) requires the residue predicate
\[
  \ClosedResidue^{\mathrm{face}}_d(R^{\mathrm{face}}_{\perp}(g)).
\]
The predicate \(\Contr_{\mathrm{dow}}(d)\) contains its negation.  The two
conditions cannot hold simultaneously, hence \(d\) is not a Grand Meson
downgrade.  If no proposed symbol satisfies the membership condition, the
class is empty.
\end{proof}

\begin{remark}[Fusion and fission]
Fusion is the closed downgrade: the active extra axes are collapsed into
the General Meson face only with an explicit residual channel.  Fission is
not a second operation.  It is the name of the contradictory downgrade
pattern in which the same projection is written while the extra axes are
discarded as if they had never contributed.  In the Grand Meson channel
discipline, this pattern is blocked by emptiness of
\(\Dow_{\mathrm{GM}}(g,m)\).  The word does not denote nuclear fission in
this paper.
\end{remark}

\section{QCD Channel-Index Lift}

The Grand Meson does not complete QCD dynamics.  It performs a conservative
channel-index lift of the six-flavor mesonic operator basis: it adds a
recoverable generation-axis indexing layer to the standard color-singlet
quark--antiquark bilinear.  It does not alter QCD color dynamics, does not
replace confinement, and does not claim a new bound state by notation
alone.  Its channel-index lift is
\[
  O_{q\bar r}\longmapsto(i,j,O_{q\bar r}),
  \qquad q\in A_i,\ r\in A_j,
\]
together with the recovery map that forgets \((i,j)\).  Let the three
flavor axes be
\[
  A_1=\{\qu,\qd\},\qquad
  A_2=\{\qc,\qs\},\qquad
  A_3=\{\qt,\qb\}.
\]

\begin{definition}[Grand Meson channel completion]
The typed channel-label layer is
\[
  \mathsf{GM}_{36}^{\mathrm{ch}}
  :=
  \left\{
    (i,j,P_{q\bar r})
    \ \middle|\
    q\in A_i,\ r\in A_j,\
    P_{q\bar r}\in\mathsf{PrePol}^{\mathrm{res}}_{q\bar r}
  \right\}.
\]
The inspectable \(36\)-channel body is the dependent product
\[
  \mathsf{PreBody}_{36}
  :=
  \prod_{q,r\in F_6}\mathsf{PrePol}^{\mathrm{res}}_{q\bar r}.
\]
An element \(G\in\mathsf{PreBody}_{36}\) has a value
\[
  G(q,\bar r)\in\mathsf{PrePol}^{\mathrm{res}}_{q\bar r}
\]
in the correct oriented channel type.  The closed \(36\)-channel body is
\[
  \mathsf{Body}_{36}^{\mathrm{cl}}
  :=
  \{\,G\in\mathsf{PreBody}_{36}\mid
  \Inact(G(q,\bar r))\ \text{or}\
  \Cl(G(q,\bar r))=\Cl_{\mathrm{GM}}
  \text{ for all }q,r\in F_6\,\}.
\]
When the closed body is intended, write
\[
  \mathsf{Body}_{36}:=\mathsf{Body}_{36}^{\mathrm{cl}},
  \qquad
  \mathsf{GM}_{36}:=\mathsf{Body}_{36}^{\mathrm{cl}}.
\]
The six-face skeleton records incident channel families; the
\(F_6\times\overline{F_6}\) dependent product is the mesonic channel body.
Its channelwise active support is
\[
  \supp_{\mathrm{ch}}(G)
  :=
  \{\,(q,\bar r)\mid \neg\Inact(G(q,\bar r))\,\},
\]
and its body-derived face support is the projection
\[
  \supp_{\mathrm{face}}(G)
  :=
  \{\,q\in F_6\mid
  (q,\bar r)\in\supp_{\mathrm{ch}}(G)
  \text{ or }(s,\bar q)\in\supp_{\mathrm{ch}}(G)
  \text{ for some }r,s\in F_6\,\}.
\]
\end{definition}

\begin{definition}[Skeleton of a body]
Define the skeleton map
\[
  \skel:\mathsf{PreBody}_{36}\longrightarrow\mathsf{Grand}^{\mathrm{raw}}
\]
by
\[
  \skel(G)(q)
  :=
  \left(
    (G(q,\bar r))_{r\in F_6},\
    (G(s,\bar q))_{s\in F_6}
  \right)
  \in\mathsf{Face}^{\mathrm{res}}_q.
\]
A pair \((g,G)\) is skeleton--body compatible when
\[
  g=\skel(G).
\]
The map \(\skel\) is injective, since each body value \(G(q,\bar r)\)
appears in the outgoing family of the \(q\)-face.  Thus a face is never
identified with a single \(q\bar r\) package; it is the incident family
extracted from the body.
\end{definition}

\begin{definition}[Glued Grand Meson skeleton]
The inspectable body-compatible skeleton is
\[
  \mathsf{PreGrand}_{\mathrm{comp}}
  :=
  \operatorname{Im}
  \bigl(\skel:\mathsf{PreBody}_{36}\to\mathsf{Grand}^{\mathrm{raw}}\bigr).
\]
The closed body-compatible Grand Meson skeleton is
\[
  \mathsf{Grand}_{\mathrm{comp}}
  :=
  \operatorname{Im}
  \bigl(\skel:\mathsf{Body}_{36}^{\mathrm{cl}}
  \to\mathsf{Grand}^{\mathrm{raw}}\bigr)
  \subseteq
  \mathsf{Grand}^{\mathrm{raw}}.
\]
An element \(g\in\mathsf{Grand}^{\mathrm{raw}}\) is glued when there exists
some \(G\in\mathsf{PreBody}_{36}\) such that \(g=\skel(G)\).  It is a
closed Grand Meson skeleton when such a witness may be chosen in
\(\mathsf{Body}_{36}^{\mathrm{cl}}\).  Equivalently, every incident
appearance of the same oriented package \(P_{q\bar r}\) agrees across the
two faces that mention it, and closed Grand Mesons additionally have no
unclosed active component.  From this point onward, unqualified
\(\mathsf{Grand}\) means the closed glued object
\(\mathsf{Grand}_{\mathrm{comp}}\).
\end{definition}

\begin{definition}[UD burial on the channel body]
Let
\[
  \mathsf{PreGM}_{36,\qu\qd}^{0,\mathrm{body}}
  :=
  \{\,G\in\mathsf{PreBody}_{36}\mid
  G(q,\bar r)=\mathbf 0_{q\bar r}[\mathrm{buried}]
  \ \text{for every }(q,\bar r)\notin
  A_Y\times\overline{A_Y}\,\}.
\]
Set
\[
  \mathsf{GM}_{36,\qu\qd}^{0,\mathrm{body}}
  :=
  \mathsf{PreGM}_{36,\qu\qd}^{0,\mathrm{body}}
  \cap
  \mathsf{Body}_{36}^{\mathrm{cl}}.
\]
Define the channel-body burial normalization
\[
  \mathcal B_{\qu\qd}:\mathsf{PreBody}_{36}\to
  \mathsf{PreGM}_{36,\qu\qd}^{0,\mathrm{body}}
\]
by
\[
  \mathcal B_{\qu\qd}(G)(q,\bar r)
  =
  \begin{cases}
    G(q,\bar r), & (q,\bar r)\in A_Y\times\overline{A_Y},\\
    \mathbf 0_{q\bar r}[\mathrm{buried}],
      & (q,\bar r)\notin A_Y\times\overline{A_Y}.
  \end{cases}
\]
Thus every cross-generation or non-UD body channel is retained as a closed
inactive residual package, not deleted and not forgotten.
The body projection is
\[
  p^{\mathrm{body}}_{\qu\qd}(G)
  :=
  G|_{A_Y\times\overline{A_Y}}
  \in\mathsf{PreBody}_{Y}.
\]
\end{definition}

\begin{definition}[Body zero extension and \(F_6\)-completion]
For \(M\in\mathsf{Body}_{Y}^{\mathrm{cl}}\), define the body zero extension
\[
  z^{\mathrm{body}}(M)\in\mathsf{Body}_{36}^{\mathrm{cl}}
\]
by
\[
  z^{\mathrm{body}}(M)(q,\bar r)
  =
  \begin{cases}
    M(q,\bar r), & (q,\bar r)\in A_Y\times\overline{A_Y},\\
    \mathcal C_{\mathrm{GM}}(\bot_{q\bar r}),
      & (q,\bar r)\notin A_Y\times\overline{A_Y}.
  \end{cases}
\]
For \(m\in\mathsf{Gen}\), define the announced six-flavor completion by
\[
  z^{\mathrm{comp}}(m)
  :=
  \mathrm{Completion}_{F_6}(m)
  :=
  \skel\!\left(z^{\mathrm{body}}(\body_Y(m))\right)
  \in\mathsf{Grand}_{\mathrm{comp}}.
\]
Equivalently,
\[
  z^{\mathrm{comp}}(m)
  =
  \mathrm{Completion}_{F_6}(m)
  =
  \mathcal C_{\mathrm{GM}}\bigl(L_{\bot}(m)\bigr),
\]
where the last expression means: preserve the UD face data and apply
\(\mathcal C_{\mathrm{GM}}\) to every missing non-UD incident channel.
\end{definition}

\begin{proposition}[Completion identities]
The local completion symbols introduced above are connected by the body
witness
\[
  \boxed{
  z^{\mathrm{comp}}(m)=\skel\!\left(z^{\mathrm{body}}(\body_Y(m))\right)
  \in\mathsf{Grand}_{\mathrm{comp}}
  }
\]
and the two identities
\[
  \boxed{
  z^{\mathrm{comp}}(m)=\mathcal C_{\mathrm{GM}}\bigl(L_{\bot}(m)\bigr)
  }
\]
for every glued General Meson
\(m\in\mathsf{Gen}=\mathsf{Gen}_{\mathrm{comp}}\), and
\[
  \boxed{
  \mathsf{Grand}_{\mathrm{comp}}
  =
  \operatorname{Im}
  \bigl(
    \skel:\mathsf{Body}_{36}^{\mathrm{cl}}\to\mathsf{Grand}^{\mathrm{raw}}
  \bigr).
  }
\]
The first identity says that zero extension is the missing-channel lift
followed by buried completion.  The second says that a Grand Meson skeleton
is closed and glued exactly when it comes from a closed \(36\)-channel body.
\end{proposition}

\begin{proof}
Since \(m\) is glued, \(M:=\body_Y(m)\) exists and satisfies
\(m=\skel_Y(M)\).  The body zero extension \(z^{\mathrm{body}}(M)\)
preserves the UD body \(M\) and sends every non-UD body channel to its buried
inactive package.  Applying \(\skel\) gives exactly the face-level zero
completion \(z^{\mathrm{comp}}(m)\).  Hence \(z^{\mathrm{comp}}(m)\) has the body witness
\(z^{\mathrm{body}}(\body_Y(m))\) and lies in
\(\operatorname{Im}(\skel|_{\mathsf{Body}_{36}^{\mathrm{cl}}})
=\mathsf{Grand}_{\mathrm{comp}}\).
The componentwise definition of \(\mathcal C_{\mathrm{GM}}\) sends each
missing non-UD channel of \(L_{\bot}(m)\) to the same buried inactive
package and leaves the UD data represented by \(m\) unchanged; this is the
same \(z^{\mathrm{comp}}(m)\).  The final identity is the definition of
\(\mathsf{Grand}_{\mathrm{comp}}\).
\end{proof}

\begin{definition}[Glued UD projection]
Define the glued projection
\[
  p_{\qu\qd}:\mathsf{Grand}_{\mathrm{comp}}\to\mathsf{Gen}
\]
by
\[
  p_{\qu\qd}(\skel(G))
  :=
  \skel_Y\!\left(p^{\mathrm{body}}_{\qu\qd}(G)\right).
\]
This is the restriction of the raw projection to glued skeletons, with the
codomain restricted to glued General Mesons.
\end{definition}

\begin{definition}[Closed UD burial subobject]
The closed UD-burial subobject is
\[
  \mathsf{Grand}_{\qu\qd}^{0,\mathrm{comp}}
  :=
  z^{\mathrm{comp}}(\mathsf{Gen})
  \subseteq
  \mathsf{Grand}_{\mathrm{comp}}.
\]
\end{definition}

\begin{proposition}[Closed General Meson recovery]
Restriction to the UD face gives an isomorphism
\[
  \mathsf{Grand}_{\qu\qd}^{0,\mathrm{comp}}\cong\mathsf{Gen}.
\]
More explicitly,
\[
  p_{\qu\qd}|_{\mathsf{Grand}_{\qu\qd}^{0,\mathrm{comp}}}
  :
  \mathsf{Grand}_{\qu\qd}^{0,\mathrm{comp}}\to\mathsf{Gen}
\]
has inverse \(z^{\mathrm{comp}}:\mathsf{Gen}\to
\mathsf{Grand}_{\qu\qd}^{0,\mathrm{comp}}\).
\end{proposition}

\begin{proof}
By definition, every element of
\(\mathsf{Grand}_{\qu\qd}^{0,\mathrm{comp}}\) has the form \(z^{\mathrm{comp}}(m)\) for a
unique \(m\in\mathsf{Gen}\).  Since \(m\) has a closed UD body witness,
\(z^{\mathrm{comp}}(m)=\skel(z^{\mathrm{body}}(\body_Y(m)))\) has a closed
\(36\)-channel body witness and therefore belongs to
\(\mathsf{Grand}_{\mathrm{comp}}\).  The glued projection returns the UD
body witness, hence \(p_{\qu\qd}(z^{\mathrm{comp}}(m))=m\).
\end{proof}

\begin{proposition}[Glued backward recovery]
For every \(m\in\mathsf{Gen}\),
\[
  p_{\qu\qd}\bigl(\mathrm{Completion}_{F_6}(m)\bigr)=m.
\]
Equivalently,
\[
  p_{\qu\qd}\circ\mathrm{Completion}_{F_6}
  =
  \mathrm{id}_{\mathsf{Gen}}.
\]
\end{proposition}

\begin{proof}
Let \(M=\body_Y(m)\).  By definition,
\[
  \mathrm{Completion}_{F_6}(m)=\skel(z^{\mathrm{body}}(M)).
\]
Applying \(p_{\qu\qd}\) restricts the completed body back to
\(A_Y\times\overline{A_Y}\), which is exactly \(M\).  Applying
\(\skel_Y\) then returns \(m\).
\end{proof}

\begin{definition}[Body downgrade residue and closure]
For \(G\in\mathsf{PreBody}_{36}\), define
\[
  R^{\mathrm{body}}_{\perp}(G)
  :=
  G|_{(F_6\times\overline{F_6})\setminus
  (A_Y\times\overline{A_Y})}
\]
and
\[
  S^{\mathrm{body}}_{\perp}(G)
  :=
  \{\,(q,\bar r)\notin A_Y\times\overline{A_Y}\mid
  G(q,\bar r)\ne\mathbf 0_{q\bar r}[\mathrm{buried}]\,\}.
\]
For a body downgrade or transition witness \(U\), the predicate
\[
  \ClosedResidue^{\mathrm{body}}_{U}
  \bigl(R^{\mathrm{body}}_{\perp}(G)\bigr)
\]
means that \(U\) carries a witness
\[
  \chi_U:S^{\mathrm{body}}_{\perp}(G)\longrightarrow
  \RCl_{\mathrm{body}}(U)
\]
and that \(\mathcal B_{\qu\qd}(G)\) sends every such channel to
\(\mathbf 0_{q\bar r}[\mathrm{buried}]\).
\end{definition}

\begin{proposition}[Body-level General Meson recovery]
Restriction to
\(A_Y\times\overline{A_Y}\) gives
\[
  \mathsf{GM}_{36,\qu\qd}^{0,\mathrm{body}}
  \cong
  \mathsf{Body}_{Y}^{\mathrm{cl}}.
\]
\end{proposition}

\begin{proof}
Every channel outside \(A_Y\times\overline{A_Y}\) is fixed to the closed
inactive package \(\mathbf 0_{q\bar r}[\mathrm{buried}]\), so an element of
\(\mathsf{GM}_{36,\qu\qd}^{0,\mathrm{body}}\) is determined exactly by its
four oriented
UD channels:
\[
  \qu\bar{\qu},\quad
  \qu\bar{\qd},\quad
  \qd\bar{\qu},\quad
  \qd\bar{\qd}.
\]
Conversely, any package assignment on these four channels extends uniquely
by buried inactive packages on the remaining \(32\) channels.
\end{proof}

\begin{proposition}[Skeleton--body burial compatibility]
For every \(G\in\mathsf{PreBody}_{36}\),
\[
  \skel(\mathcal B_{\qu\qd}(G))
  =
  \beta_{\qu\qd}(\skel(G)).
\]
Thus face-level burial and body-level burial are the same normalization
seen from two typed layers.
\end{proposition}

\begin{proof}
For \(q\in A_Y\), both sides keep the incident UD family.  For
\(q\notin A_Y\), every incident body channel of
\(\mathcal B_{\qu\qd}(G)\) is a buried inactive package, hence the
skeleton is \(\mathbf 0_q[\mathrm{buried}]\).  This is exactly the
definition of \(\beta_{\qu\qd}\) applied to \(\skel(G)\).
\end{proof}

\begin{definition}[Generation as internal direction]
Let
\[
  G_3=\{1,2,3\},
  \qquad
  H_2=\{+,-\}.
\]
Define
\[
  \Phi:G_3\times H_2\longrightarrow F_6
\]
by
\[
  (1,+)\mapsto\qu,\quad (1,-)\mapsto\qd,\quad
  (2,+)\mapsto\qc,\quad (2,-)\mapsto\qs,\quad
  (3,+)\mapsto\qt,\quad (3,-)\mapsto\qb .
\]
Then
\[
  A_i=\Phi(\{i\}\times H_2).
\]
\end{definition}

\begin{proposition}[Generation-index decomposition of the Grand Meson skeleton]
The raw six-flavor face layer decomposes as
\[
  \mathsf{Grand}^{\mathrm{raw}}
  =
  \prod_{q\in F_6}\mathsf{Face}^{\mathrm{res}}_q
  \cong
  \prod_{(i,\epsilon)\in G_3\times H_2}
  \mathsf{Face}^{\mathrm{res}}_{\Phi(i,\epsilon)}
  \cong
  \prod_{i\in G_3}\prod_{\epsilon\in H_2}
  \mathsf{Face}^{\mathrm{res}}_{\Phi(i,\epsilon)}.
\]
The glued Grand Meson \(\mathsf{Grand}_{\mathrm{comp}}\) inherits this
three-axis indexing through its inclusion into
\(\mathsf{Grand}^{\mathrm{raw}}\).  Thus the three observed quark
generations are not derived from the General Meson alone; they enter as
the fixed six-flavor input and become internal directions of the completed
skeleton.
\end{proposition}

\begin{definition}[Top-axis closure]
The third direction
\[
  A_3=\{\qt,\qb\}
\]
is not an ordinary top-meson axis.  It is a weak-virtual channel axis.
For a channel \(q\bar r\), define
\[
  \TopCh(q\bar r)
  \quad\Longleftrightarrow\quad
  (q=\qt)\ \text{or}\ (r=\qt).
\]
An ordinary mesonic readout is defined only when \(\TopCh(q\bar r)\) is
false.  If \(\TopCh(q\bar r)\) is true, the channel closes only through a
weak-virtual channel closure relative to a channel residual assignment
\(\mathcal R_{\mathrm{ch}}\in\mathsf{ChResType}\):
\[
  \mathsf{WCl}(q\bar r)\subseteq\mathcal R_{\mathrm{ch}}(q\bar r).
\]
The closure object is the weak charged-current exit available before an
ordinary top-bearing mesonic readout can be formed.  Let
\[
  d_1=\qd,\qquad d_2=\qs,\qquad d_3=\qb .
\]
\[
  \mathsf{WCl}_{L}(\qt\bar r)
  :=
  \{\,\qt\to d_j W^+\ \mathrm{with}\ V_{3j}\mid j=1,2,3\,\},
\]
and, for an anti-top-bearing channel,
\[
  \mathsf{WCl}_{R}(q\bar{\qt})
  :=
  \{\,\bar{\qt}\to\bar d_j W^-\ \mathrm{with}\ \overline{V_{3j}}
    \mid j=1,2,3\,\}.
\]
For a general channel, \(\mathsf{WCl}(q\bar r)\) is the union of all
available left and right top exits; for \(\qt\bar{\qt}\), both sides are
required.  If neither side contains a top label, \(\mathsf{WCl}(q\bar r)\)
is empty.
Thus the top axis is present in the six-flavor completion, but ordinary
mesonic readability is blocked unless the weak-virtual closure is supplied.
\end{definition}

\begin{proposition}[Unclosed top readout is GM-contradictory]
Let \(P_{q\bar r}\in\mathsf{PrePol}^{\mathrm{res}}_{q\bar r}\) be a package
whose ordinary readout claims an ordinary top-bearing meson, and let
\(\mathcal R_{\mathrm{ch}}\in\mathsf{ChResType}\).  If
\(\TopCh(q\bar r)\) holds and
\(\mathsf{WCl}(q\bar r)\nsubseteq\mathcal R_{\mathrm{ch}}(q\bar r)\), then the
ordinary-meson readout symbol is contradictory.  Equivalently,
\[
  \TopCh(q\bar r)
  \ \wedge\
  \mathsf{WCl}(q\bar r)\nsubseteq\mathcal R_{\mathrm{ch}}(q\bar r)
  \quad\Longrightarrow\quad
  \Contr_{\mathrm{top}}(P_{q\bar r};\mathcal R_{\mathrm{ch}}).
\]
\end{proposition}

\begin{definition}[Grand Meson charge-closure vector]
In the Grand Meson calculus, ``charge'' means a charge-closure vector, not
electric charge alone.  Fix a finite sector-label space
\(\mathbb R^{\Sigma_{\mathrm{GM}}}\) containing the spin-parity, threshold,
anomaly, and readout labels used in the paper, and set
\[
  \mathcal K_{\mathrm{GM}}
  :=
  \mathbb R
  \oplus\mathbb R^{F_6}
  \oplus\mathbb R^{3\times3}
  \oplus\mathbb R
  \oplus\mathbb R^{\Sigma_{\mathrm{GM}}}.
\]
Equip this finite-dimensional real vector space with a fixed weighted
inner product \(\langle-,-\rangle_W\).  The components below are embedded
into the displayed direct summands.  For any pair
\[
  \Xi=(\boldsymbol\sigma^\Xi,\mathcal R^\Xi_{\mathrm{ch}})
\]
with
\[
  \boldsymbol\sigma^\Xi=(\sigma^\Xi_{q\bar r})_{q,r\in F_6},
  \qquad
  \mathcal R^\Xi_{\mathrm{ch}}\in\mathsf{ChResType},
\]
define
\[
  \tau_{\mathrm{top}}^{\Xi}(q,\bar r)
  :=
  \begin{cases}
    1,
      & \TopCh(q\bar r)
        \ \text{and}\
        \mathsf{WCl}(q\bar r)\nsubseteq
        \mathcal R^\Xi_{\mathrm{ch}}(q\bar r),\\
    0, & \text{otherwise}.
  \end{cases}
\]
For \(q\in A_i\), \(r\in A_j\), and spin-parity sector \(\sigma\), define
\[
  \kappa_{\mathrm{GM}}^{\Xi}(q,\bar r;\sigma)
  :=
  \bigl(
    Q_q-Q_r,\
    e_q-e_r,\
    \mathbf a_{ij},\
    \tau_{\mathrm{top}}^{\Xi}(q,\bar r),\
    \chi_\sigma(q,\bar r)
  \bigr)
  \in\mathcal K_{\mathrm{GM}} .
\]
For an oriented channel \(c=(q,\bar r)\), write
\[
  \kappa_{\mathrm{GM}}^{\Xi}(c)
  :=
  \kappa_{\mathrm{GM}}^{\Xi}(q,\bar r;\sigma^\Xi_{q\bar r}).
\]
The coordinate \(\chi_\sigma(q,\bar r)\) records the spin-parity,
threshold, anomaly, and readout sector used by the package.
For each channel and sector let
\[
  \mathcal Z_{q\bar r,\sigma}\subset\mathcal K_{\mathrm{GM}}
\]
be a nonempty closed affine subspace, called the closed charge-balanced
readout locus, and let
\[
  \Pi_{q\bar r,\sigma}:\mathcal K_{\mathrm{GM}}\to
  \mathcal Z_{q\bar r,\sigma}
\]
be the unique \(W\)-orthogonal projection onto it.
\end{definition}

\begin{definition}[Charge-closure strain and stability]
The following structure is an added diagnostic layer on top of the
channel-index lift.  It is not derived from QCD dynamics or from the
existence of \(\mathsf{PreBody}_{36}\).  It supplies a closure-distance
semantics for robustness tests inside this paper.

Let \(G\in\mathsf{PreBody}_{36}\) be an inspectable Grand Meson body.  A
Grand Meson charge
assignment is a variable family
\[
  \mathbf K=(K_{q\bar r})_{q,r\in F_6},
  \qquad
  K_{q\bar r}\in\mathcal K_{\mathrm{GM}},
 \]
and the diagnostic configuration supplies the channelwise sector and
channel residual-closure assignments:
\[
  \Xi:=(\boldsymbol\sigma^\Xi,\mathcal R^\Xi_{\mathrm{ch}}),
  \qquad
  \boldsymbol\sigma^\Xi=(\sigma^\Xi_{q\bar r})_{q,r\in F_6},
\]
where \(\mathcal R^\Xi_{\mathrm{ch}}\) is a fixed channel residual-closure
assignment with \(\mathcal R^\Xi_{\mathrm{ch}}\in\mathsf{ChResType}\).
The distinguished standard assignment for \(\Xi\) is
\[
  K^{\mathrm{std},\Xi}_{q\bar r}
  :=
  \kappa_{\mathrm{GM}}^{\Xi}(q,\bar r;\sigma^\Xi_{q\bar r}).
\]
All strain, projection, and stability expressions in this section carry
\(\Xi\) explicitly.
Define channel activity by
\[
  a_G(q,\bar r)
  :=
  \begin{cases}
    0, & G(q,\bar r)=\mathbf 0_{q\bar r}[\rho]
      \ \text{for some }\rho\in\mathsf{Prov}_0,\\
    1, & \text{otherwise}.
  \end{cases}
\]
Define
\[
  \mathrm{TopOk}_{\Xi}(q\bar r)
  \quad\Longleftrightarrow\quad
  \neg\TopCh(q\bar r)
  \ \text{or}\
  \mathsf{WCl}(q\bar r)\subseteq\mathcal R^\Xi_{\mathrm{ch}}(q\bar r).
\]
The closure barrier is
\[
  \Theta_{G,\Xi}(q,\bar r)
  :=
  \begin{cases}
    0, & a_G(q,\bar r)=0,\\
    0,
      & a_G(q,\bar r)=1
        \ \text{and}\
        \Cl(G(q,\bar r))=\Cl_{\mathrm{GM}}
        \ \text{and}\
        \mathrm{TopOk}_{\Xi}(q\bar r),\\
    +\infty, & \text{otherwise}.
  \end{cases}
\]
The charge-closure imbalance of \(q\bar r\), valued in the extended
nonnegative reals, is
\[
  \mathcal I_{G,\Xi}(q,\bar r;\mathbf K)
  :=
  a_G(q,\bar r)\,
  \dist_W^2(K_{q\bar r},\mathcal Z_{q\bar r,\sigma^\Xi_{q\bar r}})
  +
  \Theta_{G,\Xi}(q,\bar r),
\]
where
\[
  \dist_W^2(K_{q\bar r},\mathcal Z_{q\bar r,\sigma^\Xi_{q\bar r}})
  :=
  \left\|
    K_{q\bar r}-\Pi_{q\bar r,\sigma^\Xi_{q\bar r}}K_{q\bar r}
  \right\|_W^2 .
\]
Write
\(\varepsilon_{G,\Xi}(q,\bar r;\mathbf K):=
\mathcal I_{G,\Xi}(q,\bar r;\mathbf K)\).
For an oriented channel \(c=(q,\bar r)\), write
\[
  \mathcal I_{G,\Xi}(c;\mathbf K)
  :=
  \mathcal I_{G,\Xi}(q,\bar r;\mathbf K).
\]
The total Grand Meson strain and stability are
\[
  \mathcal E_{G,\Xi}(\mathbf K)\in[0,+\infty]
  :=
  \sum_{q,r\in F_6}\mathcal I_{G,\Xi}(q,\bar r;\mathbf K),
  \qquad
  \mathsf{St}_{G,\Xi}(\mathbf K)
  :=
  \frac{1}{1+\mathcal E_{G,\Xi}(\mathbf K)}.
\]
Thus \(\mathsf{St}_{G,\Xi}(\mathbf K)=0\) when an unclosed channel carries the
\(+\infty\) barrier.  The imbalance is a charge-closure imbalance: electric
charge, flavor, axis-pair data, top obstruction, and the readout sector all
participate.
\end{definition}

\begin{definition}[Transition margin]
For an oriented channel \(q\bar r\), define the finite candidate target set
\[
  \mathsf{Cand}_{G,\Xi}(q\bar r;\mathbf K)
  :=
  \{\,s\bar t\mid
  \mathcal I_{G,\Xi}(q,\bar r;\mathbf K)<+\infty,\
  \mathcal I_{G,\Xi}(s,\bar t;\mathbf K)<+\infty\,\}.
\]
For \(s\bar t\in\mathsf{Cand}_{G,\Xi}(q\bar r;\mathbf K)\), define the Grand
Meson transition margin
\[
  M_{G,\Xi}(q\bar r\to s\bar t;\mathbf K)
  :=
  \mathcal I_{G,\Xi}(s,\bar t;\mathbf K)
  -
  \mathcal I_{G,\Xi}(q,\bar r;\mathbf K).
\]
Among closed candidate targets, the internally preferred directions in this
diagnostic order are the minimizers
\[
  \operatorname*{arg\,min}_{s\bar t\in\mathsf{Cand}_{G,\Xi}(q\bar r;\mathbf K)}
  M_{G,\Xi}(q\bar r\to s\bar t;\mathbf K).
\]
This is an internal preference order, not a decay-rate prediction.
\end{definition}

\begin{definition}[Projected discontinuity certificate]
On the product space
\[
  \prod_{q,r\in F_6}\mathcal K_{\mathrm{GM}},
\]
use the product weighted inner product
\[
  \langle H,H'\rangle_{\Pi W}
  :=
  \sum_{q,r\in F_6}
  \langle H_{q\bar r},H'_{q\bar r}\rangle_W .
\]
Let \(\mathsf{Sm}_{G,\Xi}\) be the finite smooth projection
stratum on which
\(\mathcal E_{G,\Xi}(\mathbf K)<+\infty\) and every projection
\(\Pi_{q\bar r,\sigma^\Xi_{q\bar r}}\) appearing in an active channel is
differentiable.
The UD-visible strain is
\[
  \mathcal E_{Y,G,\Xi}(\mathbf K)
  :=
  \sum_{q,r\in A_Y}\mathcal I_{G,\Xi}(q,\bar r;\mathbf K),
\]
and the non-UD residual strain opened by the Grand Meson body is
\[
  \mathcal E_{\perp,G,\Xi}(\mathbf K)
  :=
  \mathcal E_{G,\Xi}(\mathbf K)-\mathcal E_{Y,G,\Xi}(\mathbf K)
  =
  \sum_{(q,\bar r)\notin A_Y\times\overline{A_Y}}
  \mathcal I_{G,\Xi}(q,\bar r;\mathbf K).
\]
Define the static discontinuity certificate
\[
  \mathfrak D_{G,\Xi}:\mathsf{Sm}_{G,\Xi}\to
  [0,+\infty)\times
  \prod_{q,r\in F_6}\mathcal K_{\mathrm{GM}},
  \qquad
  \mathfrak D_{G,\Xi}(\mathbf K)
  :=
  \left(
    \mathcal E_{\perp,G,\Xi}(\mathbf K),\
    \nabla\mathcal E_{\perp,G,\Xi}(\mathbf K)
  \right).
\]
It measures not a dangerous object, but a projected network imbalance: the
part of the charge-closure network that is invisible before the non-UD axes
are opened.
\end{definition}

\begin{definition}[Fuse set and fuse normal form]
Fix a readout threshold \(\epsilon_{\mathrm{fuse}}>0\).  After the non-UD
axes are opened, define the fuse set
\[
  \Omega_{\mathrm{fuse}}(G,\Xi,\mathbf K)
  :=
  \{\,(q,\bar r)\mid
  \mathcal I_{G,\Xi}(q,\bar r;\mathbf K)=+\infty
  \ \text{or}\
  \mathcal I_{G,\Xi}(q,\bar r;\mathbf K)\ge\epsilon_{\mathrm{fuse}}\,\}.
\]
The non-UD residual fuse set is
\[
  \Omega_{\perp}(G,\Xi,\mathbf K)
  :=
  \Omega_{\mathrm{fuse}}(G,\Xi,\mathbf K)
  \cap
  \bigl((F_6\times\overline{F_6})
  \setminus(A_Y\times\overline{A_Y})\bigr).
\]
The associated residual fission network is the directed graph
\[
  E_{\perp}(G,\Xi,\mathbf K)
  :=
  \{\,(q,r)\in F_6\times F_6\mid
  (q,\bar r)\in\Omega_{\perp}(G,\Xi,\mathbf K)\,\}.
\]
\[
  \mathcal N_{\perp}(G,\Xi,\mathbf K)
  :=
  (F_6,E_{\perp}(G,\Xi,\mathbf K)).
\]
The fuse normal form is the body map
\[
  \mathsf{Fuse}_{G,\Xi,\mathbf K}\in\mathsf{Body}_{36}^{\mathrm{cl}}
  \quad\text{defined by}\quad
  \mathsf{Fuse}_{G,\Xi,\mathbf K}(q,\bar r)
  :=
  \begin{cases}
    \mathbf 0_{q\bar r}[\mathrm{fuse}],
      & (q,\bar r)\in\Omega_{\mathrm{fuse}}(G,\Xi,\mathbf K),\\
    G(q,\bar r), & \text{otherwise}.
  \end{cases}
\]
This is not a destructive physical process.  It is the Grand Meson closure
response that turns a detected charge-closure imbalance into a closed
inactive residual package.
The codomain is closed: every fuse edge is replaced by
\(\mathbf 0[\mathrm{fuse}]\), while every non-fuse active edge has finite
barrier and therefore satisfies the Grand closure suite.
\end{definition}

\begin{proposition}[Closedness of the fuse normal form]
For every \(G\in\mathsf{PreBody}_{36}\), diagnostic configuration \(\Xi\),
and \(\mathbf K\), the body map
\(\mathsf{Fuse}_{G,\Xi,\mathbf K}\) lies in
\(\mathsf{Body}_{36}^{\mathrm{cl}}\).
\end{proposition}

\begin{proof}
If \((q,\bar r)\in\Omega_{\mathrm{fuse}}(G,\Xi,\mathbf K)\), the output
component is \(\mathbf 0_{q\bar r}[\mathrm{fuse}]\), hence a closed
inactive residual package.  If
\((q,\bar r)\notin\Omega_{\mathrm{fuse}}(G,\Xi,\mathbf K)\), then
\(\mathcal I_{G,\Xi}(q,\bar r;\mathbf K)<+\infty\).  Since the only
infinite contribution to \(\mathcal I_{G,\Xi}\) is the closure barrier,
\(\Theta_{G,\Xi}(q,\bar r)=0\).  Therefore the component is either inactive,
or it is active and satisfies \(\Cl=\Cl_{\mathrm{GM}}\) together with
\(\mathrm{TopOk}_{\Xi}\).  Thus every output component is closed.
\end{proof}

\begin{definition}[Finite readout load]
Let \(H\in\mathsf{PreBody}_{36}\) be any proposed post-opening body map
that agrees with \(G\) outside
\(\Omega_{\mathrm{fuse}}(G,\Xi,\mathbf K)\).  Define the residual
readout load on an imbalanced edge by
\[
  \lambda_{G,\Xi,\mathbf K}^{H}(q,\bar r)
  :=
  \begin{cases}
    0,
      & H(q,\bar r)=\mathbf 0_{q\bar r}[\mathrm{fuse}],\\
    +\infty,
      & H(q,\bar r)\ne\mathbf 0_{q\bar r}[\mathrm{fuse}],
  \end{cases}
  \qquad
  (q,\bar r)\in\Omega_{\mathrm{fuse}}(G,\Xi,\mathbf K).
\]
The total residual readout load is
\[
  \mathsf{Load}_{G,\Xi,\mathbf K}(H)
  :=
  \sum_{(q,\bar r)\in\Omega_{\mathrm{fuse}}(G,\Xi,\mathbf K)}
  \lambda_{G,\Xi,\mathbf K}^{H}(q,\bar r).
\]
A finite Grand Meson readout circuit is one whose residual readout load is
finite.
For a finite cutoff \(L>0\), define
\[
  \lambda_{G,\Xi,\mathbf K}^{H,L}(q,\bar r)
  :=
  \begin{cases}
    0,
      & H(q,\bar r)=\mathbf 0_{q\bar r}[\mathrm{fuse}],\\
    L,
      & H(q,\bar r)\ne\mathbf 0_{q\bar r}[\mathrm{fuse}],
  \end{cases}
\]
and
\[
  \mathsf{Load}^{(L)}_{G,\Xi,\mathbf K}(H)
  :=
  \sum_{(q,\bar r)\in\Omega_{\mathrm{fuse}}(G,\Xi,\mathbf K)}
  \lambda_{G,\Xi,\mathbf K}^{H,L}(q,\bar r).
\]
\end{definition}

\begin{definition}[Body transition space]
A body transition symbol is written \(U:G\to G'\), with
\(G,G'\in\mathsf{PreBody}_{36}\).  Its changed body support is
\[
  \Delta_{\mathrm{body}}(U)
  :=
  \{\,(q,\bar r)\mid G(q,\bar r)\ne G'(q,\bar r)\,\}.
\]
After a fuse network has been opened, the support that must be closed is
not only the changed support but also the visible fuse support:
\[
  \Sigma_{\mathrm{body}}(U;G,\Xi,\mathbf K)
  :=
  \Delta_{\mathrm{body}}(U)
  \cup
  \Omega_{\mathrm{fuse}}(G,\Xi,\mathbf K).
\]
The body transition space is
\[
  \Mor^{\mathrm{body}}_{\mathrm{GM}}(G,\Xi,\mathbf K)
  :=
  \{\,U:G\to G'\mid
  \Sigma_{\mathrm{body}}(U;G,\Xi,\mathbf K)
  \subseteq\RCl_{\mathrm{body}}(U)\,\}.
\]
The body-transition contradiction predicate is
\[
  \Contr_{\mathrm{tr}}(U;G,\Xi,\mathbf K)
  :=
  \Sigma_{\mathrm{body}}(U;G,\Xi,\mathbf K)
  \setminus\RCl_{\mathrm{body}}(U)
  \ne\varnothing .
\]
\end{definition}

\begin{theorem}[Deterministic charge-closure strain diagnostic]
Fix an inspectable Grand Meson body \(G\), a diagnostic configuration
\(\Xi\), and a Grand Meson charge
assignment \(\mathbf K\in\mathsf{Sm}_{G,\Xi}\).  Then the following data
are determined uniquely:
\[
  \mathsf{St}_{G,\Xi}(\mathbf K),\qquad
  \mathfrak D_{G,\Xi}(\mathbf K),\qquad
  M_{G,\Xi}(q\bar r\to s\bar t;\mathbf K),
\]
for every finite candidate \(s\bar t\in
\mathsf{Cand}_{G,\Xi}(q\bar r;\mathbf K)\).  On every finite smooth projection
stratum, for a variation
\(h=(h_{q\bar r})_{q,r\in F_6}\),
\[
  D\mathcal E_{G,\Xi}(\mathbf K)[h]
  =
  2\sum_{q,r\in F_6}
  a_G(q,\bar r)
  \left\langle
    K_{q\bar r}-\Pi_{q\bar r,\sigma^\Xi_{q\bar r}}K_{q\bar r},\
    h_{q\bar r}
    -D\Pi_{q\bar r,\sigma^\Xi_{q\bar r}}(K_{q\bar r})[h_{q\bar r}]
  \right\rangle_W .
\]
Consequently
\[
  D\mathsf{St}_{G,\Xi}(\mathbf K)[h]
  =
  -\mathsf{St}_{G,\Xi}(\mathbf K)^2
  D\mathcal E_{G,\Xi}(\mathbf K)[h].
\]
If the channel charges are functions of a common parameter
\(\theta\), namely \(\mathbf K=\mathbf K(\theta)\), then
\[
  \frac{d}{d\theta}\mathcal E_{G,\Xi}(\mathbf K(\theta))
  =
  D\mathcal E_{G,\Xi}(\mathbf K(\theta))
  \left[\frac{d\mathbf K}{d\theta}\right].
\]
Thus a change in one physical parameter propagates deterministically
through exactly the channels whose charge-closure vectors depend on that
parameter.  No extra prohibition rule is required: an unclosed top-bearing
or otherwise unclosed active channel receives the \(+\infty\) barrier and
therefore cannot inhabit a stable Grand Meson transition.

Finally, the UD projection detects exactly the UD-visible part and no more:
for any \(\mathbf K,\mathbf K'\) with
\[
  K_{q\bar r}=K'_{q\bar r}
  \qquad(q,r\in A_Y),
\]
one has
\[
  \mathcal E_{Y,G,\Xi}(\mathbf K)=\mathcal E_{Y,G,\Xi}(\mathbf K'),
  \qquad
  D\mathcal E_{Y,G,\Xi}(\mathbf K)=D\mathcal E_{Y,G,\Xi}(\mathbf K')
  \ \text{on }A_Y\times\overline{A_Y}.
\]
Any change in
\[
  \mathcal E_{G,\Xi}-\mathcal E_{Y,G,\Xi}
  =
  \mathcal E_{\perp,G,\Xi}
\]
is therefore statically invisible to the General Meson and becomes
verifiable only after the non-UD axes are opened.  Along any differentiable
path \(\gamma:[0,1]\to\mathsf{Sm}_{G,\Xi}\),
\[
  \int_{\gamma}D\mathcal E_{G,\Xi}
  -
  \int_{\gamma}D\mathcal E_{Y,G,\Xi}
  =
  \mathcal E_{\perp,G,\Xi}(\gamma(1))
  -
  \mathcal E_{\perp,G,\Xi}(\gamma(0)).
\]
Thus a projected differential or integral mismatch is exactly the non-UD
residual certificate \(\mathfrak D_{G,\Xi}\).  Instability in this calculus is
not assigned by a name; it is the nonzero, threshold-level, or infinite
charge-closure imbalance carried by typed mesonic channels.
\end{theorem}

\begin{proof}
The activity \(a_G\), the projection data
\(\Pi_{q\bar r,\sigma^\Xi_{q\bar r}}\), the balanced loci
\(\mathcal Z_{q\bar r,\sigma^\Xi_{q\bar r}}\), and the barrier
\(\Theta_{G,\Xi}\) are functions of the fixed data
\((G,\Xi,\mathbf K)\).
Hence every channel imbalance \(\mathcal I_{G,\Xi}(q,\bar r;\mathbf K)\), their
sum \(\mathcal E_{G,\Xi}(\mathbf K)\), the UD-visible sum
\(\mathcal E_{Y,G,\Xi}(\mathbf K)\), the residual sum
\(\mathcal E_{\perp,G,\Xi}(\mathbf K)\), the certificate
\(\mathfrak D_{G,\Xi}(\mathbf K)\), the stability
\(\mathsf{St}_{G,\Xi}(\mathbf K)\), and every transition margin
\(M_{G,\Xi}\) are uniquely determined.

On a finite smooth projection stratum,
\[
  \mathcal I_{G,\Xi}(q,\bar r;\mathbf K)
  =
  a_G(q,\bar r)
  \|K_{q\bar r}-\Pi_{q\bar r,\sigma^\Xi_{q\bar r}}K_{q\bar r}\|_W^2 .
\]
Differentiating this weighted square gives the displayed formula for
\(D\mathcal E_{G,\Xi}\).  Since
\(\mathsf{St}_{G,\Xi}=(1+\mathcal E_{G,\Xi})^{-1}\), the chain rule gives the displayed
formula for \(D\mathsf{St}_{G,\Xi}\).  If a required closure is missing,
\(\Theta_{G,\Xi}=+\infty\); then the channel is not a finite stable transition
candidate inside the Grand Meson calculus.

The UD-visible strain \(\mathcal E_{Y,G,\Xi}\) is a sum over
\(A_Y\times\overline{A_Y}\), so it depends only on the UD restriction of
\(\mathbf K\).  Therefore two assignments with the same UD restriction have
the same \(\mathcal E_{Y,G,\Xi}\) and the same UD differential.  Subtracting
\(\mathcal E_{Y,G,\Xi}\) from \(\mathcal E_{G,\Xi}\) leaves exactly the sum of all non-UD
channel imbalances, which is \(\mathcal E_{\perp,G,\Xi}\).  Exactness of the
differential of the scalar strain along \(\gamma\) gives the displayed
integral mismatch.  Thus the opened Grand Meson axes do not add a rhetorical
warning; they add a static certificate for the residual imbalance that the
UD projection cannot see.
\end{proof}

\section{Finite Fuse Normalization}

Finite fuse normalization is the finite-readout form of the Grand Meson
closure discipline.
Once a charge-closure fission network is made visible by opening the
non-UD axes, the network cannot remain as active readout inside a finite
Grand Meson circuit.  It automatically normalizes to closed fuse residual
packages; if one insists on keeping it active, the readout load becomes
non-finite.

\begin{theorem}[Finite fuse normal form]
Assume all channels have been safely opened, meaning that every
\((q,\bar r)\in F_6\times\overline{F_6}\) is typed either by an active
package in \(\mathsf{Pol}_{q\bar r}\) or by an inactive package
\(\mathbf 0_{q\bar r}[\rho]\in\mathsf{Pol}^{\mathrm{res}}_{q\bar r}\).
If
\[
  \Omega_{\mathrm{fuse}}(G,\Xi,\mathbf K)\ne\varnothing,
\]
then the finite Grand Meson readout circuit has a unique normal form on the
opened imbalanced network:
\[
  \mathsf{Load}_{G,\Xi,\mathbf K}(H)<+\infty
  \quad\Longleftrightarrow\quad
  H(q,\bar r)=\mathsf{Fuse}_{G,\Xi,\mathbf K}(q,\bar r)
  \ \text{for all }(q,\bar r)\in\Omega_{\mathrm{fuse}}(G,\Xi,\mathbf K).
\]
Thus the channel does not decide to cut itself; within the finite-load
semantics defined here, any non-fuse value has infinite residual readout
load.

Equivalently, no Grand Meson body transition may ignore the opened
imbalance.  Let \(U:G\to G'\) preserve the UD body projection and leave at
least one
imbalanced edge unclosed:
\[
  p^{\mathrm{body}}_{\qu\qd}(G')=p^{\mathrm{body}}_{\qu\qd}(G),
  \qquad
  \Omega_{\mathrm{fuse}}(G,\Xi,\mathbf K)
  \setminus\RCl_{\mathrm{body}}(U)\ne\varnothing .
\]
Then
\[
  U\notin\Mor^{\mathrm{body}}_{\mathrm{GM}}(G,\Xi,\mathbf K),
  \qquad
  \Contr_{\mathrm{tr}}(U;G,\Xi,\mathbf K).
\]
Moreover, \(\mathsf{Fuse}_{G,\Xi,\mathbf K}\) deterministically closes every
opened fuse edge:
\[
  (q,\bar r)\in\Omega_{\mathrm{fuse}}(G,\Xi,\mathbf K)
  \quad\Longrightarrow\quad
  \mathsf{Fuse}_{G,\Xi,\mathbf K}(q,\bar r)
  =
  \mathbf 0_{q\bar r}[\mathrm{fuse}].
\]
In a finite cutoff semantics where \(+\infty\) is replaced by \(L\), any
body map \(H\) leaving \(k\) fuse edges unfused has
\[
  \mathsf{Load}^{(L)}_{G,\Xi,\mathbf K}(H)\ge kL .
\]
Hence the computational or cognitive burden of retaining the large-scale
fission network as active readout cannot remain bounded as \(L\to\infty\).
Once the opened charge-closure imbalance is visible, the finite readout
circuit automatically collapses to the closed fuse residual form.
\end{theorem}

\begin{proof}
Safe opening places every oriented channel in the typed body
\(\mathsf{PrePol}^{\mathrm{res}}_{q\bar r}\), so every fuse edge in
\(\Omega_{\mathrm{fuse}}(G,\Xi,\mathbf K)\) is a readable element of the Grand
Meson body rather than a missing symbol.  By definition of the residual
readout load, each fuse edge contributes \(0\) exactly when its post-opening
value is \(\mathbf 0_{q\bar r}[\mathrm{fuse}]\), and contributes
\(+\infty\) otherwise.  Therefore a proposed body map has finite load
exactly when it agrees with \(\mathsf{Fuse}_{G,\Xi,\mathbf K}\) on every edge of
\(\Omega_{\mathrm{fuse}}(G,\Xi,\mathbf K)\).  This proves uniqueness of the
finite normal form.

If a transition \(U\) preserves the UD body projection while leaving some
\((q,\bar r)\in\Omega_{\mathrm{fuse}}(G,\Xi,\mathbf K)\) outside
\(\RCl_{\mathrm{body}}(U)\),
then the changed or retained residual support is not contained in the
residual closure set required for membership in
\(\Mor^{\mathrm{body}}_{\mathrm{GM}}(G,\Xi,\mathbf K)\).  By the definition of
the opened body transition space,
\(U\notin\Mor^{\mathrm{body}}_{\mathrm{GM}}(G,\Xi,\mathbf K)\), and by the
definition of the contradiction predicate the same unclosed edge witnesses
\(\Contr_{\mathrm{tr}}(U;G,\Xi,\mathbf K)\).

The displayed implication for \(\mathsf{Fuse}_{G,\Xi,\mathbf K}\) is its
definition.  For every edge in \(\Omega_{\mathrm{fuse}}\), the output is
\(\mathbf 0_{q\bar r}[\mathrm{fuse}]\), which belongs to
\(\mathsf{Pol}^{\mathrm{res}}_{q\bar r}\) and satisfies
\(\Cl(\mathbf 0_{q\bar r}[\mathrm{fuse}])=\Cl_{\mathrm{GM}}\).  For every
edge outside \(\Omega_{\mathrm{fuse}}\), the channel is left unchanged.
Hence the operation closes every detected fuse edge, while an already
fuse-tagged inactive input outside \(\Omega_{\mathrm{fuse}}\) is not used
as evidence that the edge belongs to the fuse set.  Under a finite cutoff
\(L\), each of the \(k\) unfused fuse edges
contributes at least \(L\) to the load, giving the bound
\(\mathsf{Load}^{(L)}_{G,\Xi,\mathbf K}(H)\ge kL\).  The load is therefore
unbounded in the limit \(L\to\infty\).
\end{proof}

\begin{definition}[Grand Meson decay readout]
For a finite final readout family
\(\mathcal F=\{((q_y,\bar r_y),\eta_y)\}\), where each
\((q_y,\bar r_y)\) is a typed oriented output channel and
\(\eta_y\in\{\pm1\}\), write
\[
  \kappa_{\mathrm{GM}}^{\Xi}(\mathcal F)
  :=
  \sum_{((q_y,\bar r_y),\eta_y)\in\mathcal F}
  \eta_y\,
  \kappa_{\mathrm{GM}}^{\Xi}
  (q_y,\bar r_y;\sigma^\Xi_{q_y\bar r_y}),
  \qquad
  \mathcal I_{G,\Xi}(\mathcal F;\mathbf K)
  :=
  \sum_{((q_y,\bar r_y),\eta_y)\in\mathcal F}
  \mathcal I_{G,\Xi}(q_y,\bar r_y;\mathbf K).
\]
A Grand Meson decay readout of an active channel \(c=(q,\bar r)\) into
\(\mathcal F_c\) is a closed readout family satisfying
\[
  \kappa_{\mathrm{GM}}^{\Xi}(c)
  =
  \kappa_{\mathrm{GM}}^{\Xi}(\mathcal F_c)
  +
  R^{\kappa}_{\mathrm{closed}},
  \qquad
  \mathcal I_{G,\Xi}(\mathcal F_c;\mathbf K)<\mathcal I_{G,\Xi}(c;\mathbf K),
\]
where \(R^{\kappa}_{\mathrm{closed}}\in\mathcal K_{\mathrm{GM}}\) is the
charge-closure vector of a closed residual record.  For a channel \(c\),
write
\[
  R_c^{\mathrm{fuse}}
  :=
  \mathbf 0_c[\mathrm{fuse}]
\]
for the fuse residual record of \(c\).
\end{definition}

\begin{theorem}[Fuse residual attached to a declared decay readout]
Let \(c=(q,\bar r)\) be an active mesonic channel with
\(c\in\Omega_{\mathrm{fuse}}(G,\Xi,\mathbf K)\).  If there exists a Grand
Meson decay readout family \(\mathcal F_c\), then every finite Grand Meson
readout \(H\) of \(c\) has the fuse residual record as its channel value:
\[
  H(c)=R_c^{\mathrm{fuse}}.
\]
In the present calculus, the declared decay readout is represented not as
deletion but as a fuse residual record attached to a closed readout family.
The family \(\mathcal F_c\) remains part of the separately declared closed
readout relation above.
\end{theorem}

\begin{proof}
Since \(c\in\Omega_{\mathrm{fuse}}(G,\Xi,\mathbf K)\), the finite fuse normal
form says that any finite readout must agree with the fuse normal form
on \(c\).  Hence \(H(c)=\mathbf 0_c[\mathrm{fuse}]=R_c^{\mathrm{fuse}}\).
The assumed family \(\mathcal F_c\) is not derived from the zero object; it
is an additional closed readout relation whose charge vector is conserved
up to \(R^{\kappa}_{\mathrm{closed}}\) and whose imbalance is strictly
lower.
\end{proof}

\begin{conjecture}[Possible diagnostic comparison with physical decay widths]
For ordinary non-top mesonic channels for which a Standard Model decay
amplitude exists, the Grand Meson imbalance
\(\mathcal I_{G,\Xi}(q,\bar r;\mathbf K)\) is a closure-index shadow of the
physical decay width.  This is a proposed external calibration problem, not
a result of the Grand Meson calculus.  More precisely, after fixing the spin-parity sector
and available final states, there is a monotone readout functional
\(\mathcal R\) such that
\[
  \Gamma_{\mathrm{phys}}(q\bar r\to f)
  =
  \mathcal R\!\left(
    \mathcal I_{G,\Xi}(q,\bar r;\mathbf K),\
    \rho_f,\
    |\mathcal A_{\mathrm{SM}}(q\bar r\to f)|^2
  \right),
\]
where \(\rho_f\) is the final-state phase space and
\(\mathcal A_{\mathrm{SM}}\) is the corresponding Standard Model amplitude.
This conjecture does not replace the Standard Model decay formula; it asks
whether the Grand Meson fuse index can be read as a closure layer above the
ordinary amplitude.
\end{conjecture}

\begin{definition}[Anti-face fission]
Let the opposite face on the same generation axis be
\[
  \op(\Phi(i,\epsilon)):=\Phi(i,-\epsilon),
  \qquad i\in G_3,\ \epsilon\in H_2 .
\]
For a mesonic channel \(O_{q\bar r}\), the anti-quark side is the charge
conjugate \(\bar r\).  It is not the opposite Grand Meson face
\(\overline{\op(r)}\).  Define the anti-face fission candidate by
\[
  \Fis_{\bar F}(O_{q\bar r})
  :=
  O_{q\,\overline{\op(r)}} .
\]
This symbol is not a new physical process.  It is the diagnostic pattern in
which the anti-quark side of a channel is replaced by the opposite
Grand Meson face on the same generation axis.
\end{definition}

\begin{axiom}[Sector-respecting identity]
Grand Meson identity preserves the charge--flavor fingerprint:
\[
  O_{q\bar r}\equiv_{\mathrm{GM}} O_{s\bar t}
  \quad\Longrightarrow\quad
  \nu_{\mathrm{QCD}}(q,\bar r;\sigma)
  =
  \nu_{\mathrm{QCD}}(s,\bar t;\sigma).
\]
Thus two distinct quantum-number sectors may be related by an explicit
transition with closed residue, but they may not be silently identified.
\end{axiom}

\begin{proposition}[Anti-face fission is a Grand Meson contradiction]
Let
\[
  \kappa(q,\bar r):=(Q_q-Q_r,\ e_q-e_r)
\]
be the charge--flavor fingerprint of the mesonic channel, where \(Q_q\) is
the electric charge of \(q\) and \(e_q\) is its flavor unit.  If
\[
  R_{\bar F}(q,\bar r)
  :=
  \kappa(q,\bar r)-\kappa(q,\overline{\op(r)})
  \ne 0
\]
then identifying \(O_{q\bar r}\) with \(\Fis_{\bar F}(O_{q\bar r})\) is
contradictory:
\[
  O_{q\bar r}\equiv_{\mathrm{GM}} \Fis_{\bar F}(O_{q\bar r})
  \quad\Longrightarrow\quad
  \Contr_{\bar F}
  \bigl(O_{q\bar r}\equiv_{\mathrm{GM}}\Fis_{\bar F}(O_{q\bar r})\bigr).
\]
\end{proposition}

\begin{proof}
The Grand Meson readout preserves the ordered pair consisting of the quark
side and the anti-quark side.  Replacing \(\bar r\) by
\(\overline{\op(r)}\) changes the channel fingerprint by
\(R_{\bar F}(q,\bar r)\).  When this residual fingerprint is nonzero, the
two channels lie in distinct charge--flavor sectors, so the proposed
identification cannot inhabit the Grand Meson readout space.
\end{proof}

\begin{remark}[Examples]
For the light pion channel, anti-face fission sends
\[
  O_{\qu\bar{\qd}}
  \longmapsto
  O_{\qu\bar{\qu}} .
\]
The electric charge changes from \(Q_{\qu}-Q_{\qd}=+1\) to
\(Q_{\qu}-Q_{\qu}=0\), so the residual fingerprint is nonzero.  For a
cross-generation channel,
\[
  O_{\qu\bar{\qs}}
  \longmapsto
  O_{\qu\bar{\qc}},
\]
the same block occurs: \(Q_{\qu}-Q_{\qs}=+1\), whereas
\(Q_{\qu}-Q_{\qc}=0\).  On the third axis,
\[
  O_{\qu\bar{\qb}}
  \longmapsto
  O_{\qu\bar{\qt}},
\]
the flipped readout also enters the top-axis closure condition above.
Thus the Grand Meson is not merely an untyped relabeling: it adds typed
closure tests that expose wrong anti-face identifications.  The flipped
symbol may only be treated as a distinct channel with its own package and
quantum fingerprint.
\end{remark}

\begin{remark}[Worked channel table]
The following examples show that the completion is operational rather than
merely decorative.  ``Ord.'' means ordinary hadronic meson readout, and
\(R_{\perp}\) is the residual axis content under downgrade to the
\(\qu\leftrightarrow\qd\) face.
\begin{center}
\small
\begin{tabular}{@{}llllll@{}}
channel & \(q\bar r\) & axes & ord. & top & anti-face test / \(R_{\perp}\)\\
\hline
\(\pi^+\) & \(\qu\bar{\qd}\) & \((1,1)\) & yes & no
  & \(\qu\bar{\qu}:\ Q +1\to0;\ R_{\perp}=0\)\\
\(K^+\) & \(\qu\bar{\qs}\) & \((1,2)\) & yes & no
  & \(\qu\bar{\qc}:\ Q +1\to0;\ R_{\perp}=A_2\)\\
\(D^0\) & \(\qc\bar{\qu}\) & \((2,1)\) & yes & no
  & \(\qc\bar{\qd}:\ Q 0\to+1;\ R_{\perp}=A_2\)\\
\(D_s^+\) & \(\qc\bar{\qs}\) & \((2,2)\) & yes & no
  & \(\qc\bar{\qc}:\ Q +1\to0;\ R_{\perp}=A_2\)\\
\(B^-\) & \(\qb\bar{\qu}\) & \((3,1)\) & yes & no
  & \(\qb\bar{\qd}:\ Q -1\to0;\ R_{\perp}=A_3\)\\
\(J/\psi\) & \(\qc\bar{\qc}\) & \((2,2)\) & yes & no
  & \(\qc\bar{\qs}:\ Q 0\to+1;\ R_{\perp}=A_2\)\\
\(\Upsilon\) & \(\qb\bar{\qb}\) & \((3,3)\) & yes & no
  & \(\qb\bar{\qt}:\ Q 0\to-1;\ R_{\perp}=A_3\)\\
\(\qt\bar{\qb}\) & \(\qt\bar{\qb}\) & \((3,3)\) & no & \(\mathsf{WCl}\)
  & \(\qt\bar{\qt}:\ Q +1\to0;\ R_{\perp}=A_3\)\\
\(\qu\bar{\qt}\) & \(\qu\bar{\qt}\) & \((1,3)\) & no & \(\mathsf{WCl}\)
  & \(\qu\bar{\qb}:\ Q 0\to+1;\ R_{\perp}=A_3\)
\end{tabular}
\end{center}
The first seven rows are ordinary QCD mesonic readouts after closure.  The
last two are not ordinary hadronic mesons in this framework; they are
top-bearing weak-virtual channels.  In every row, the anti-face candidate
changes the charge--flavor sector, so an attempted identification is a
\(\Contr_{\bar F}\) witness unless the residual channel is explicitly
closed by a distinct transition.
\end{remark}

\begin{definition}[Grand Meson CKM lift]
Let
\[
  U_L=(\qu_L,\qc_L,\qt_L)^T,\qquad
  D_L=(\qd_L,\qs_L,\qb_L)^T,
\]
and let \(V_{\mathrm{CKM}}=(V_{ij})\in U(3)\) be the charged-current
flavor-mixing matrix.  The ordinary weak current is
\[
  J^\mu_+
  =
  \bar U_L\gamma^\mu V_{\mathrm{CKM}}D_L
  =
  \sum_{i,j=1}^{3}V_{ij}\,\bar u_{iL}\gamma^\mu d_{jL}.
\]
The Grand Meson lift places each CKM coefficient on its axis pair:
\[
  \Gamma_{\mathrm{GM}}^{\mathrm{CKM}}(V_{ij})
  :=
  (i,j,V_{ij}).
\]
For a channel package \(P_{q\bar r}\), the CKM closure predicate
\(\CKMCl(P_{q\bar r})\) is not evaluated on the meson axis pair
\((q,\bar r)\) itself.  It is evaluated on each weak charged-current edge
actually used inside the package.  If such an edge has the form
\(\bar u_{iL}\gamma^\mu d_{jL}\), then that edge must be annotated by
\((i,j,V_{ij})\) and must recover \(V_{ij}\) after forgetting the Grand
Meson labels.  If the package uses no weak charged-current edge, the CKM
predicate is vacuous.
\end{definition}

\begin{proposition}[CKM recovery]
Let \(\pi_{\mathrm{CKM}}(i,j,V_{ij})=V_{ij}\).  Then forgetting the Grand
Meson axis labels recovers the ordinary CKM current:
\[
  \sum_{i,j}\pi_{\mathrm{CKM}}
  \bigl(\Gamma_{\mathrm{GM}}^{\mathrm{CKM}}(V_{ij})\bigr)
  \bar u_{iL}\gamma^\mu d_{jL}
  =
  J^\mu_+ .
\]
Thus the Grand Meson does not derive the CKM matrix.  It annotates the
charged-current terms by generation-axis labels and verifies that forgetting
those labels recovers the ordinary weak current.  CKM mixing is therefore a
required weak-current closure layer, not a modification of QCD color
dynamics.
\end{proposition}

The ordinary QCD mesonic operator basis is
\[
  \mathsf Q_{\mathrm{mes}}
  :=
  \left\{
    O^{\Gamma_\sigma}_{q\bar r}(x)
    =
    \sum_{a=1}^{3}\bar r_a(x)\Gamma_\sigma q^a(x)
    \ \middle|\ q,r\in F_6,\ \sigma\ \text{a spin-parity sector}
  \right\}.
\]
Standard channels are recovered inside this basis, for example
\[
  \pi^+\sim O_{\qu\bar{\qd}},\quad
  K^+\sim O_{\qu\bar{\qs}},\quad
  D^0\sim O_{\qc\bar{\qu}},\quad
  B^-\sim O_{\qb\bar{\qu}},
\]
and
\[
  J/\psi\sim O_{\qc\bar{\qc}},
  \qquad
  \Upsilon\sim O_{\qb\bar{\qb}},
  \qquad
  \eta,\eta'\sim
  \mathrm{span}\{O_{\qu\bar{\qu}},O_{\qd\bar{\qd}},O_{\qs\bar{\qs}}\}.
\]
Thus cross-generation mesons such as \(u\bar s\), \(c\bar d\), \(b\bar u\),
and \(c\bar s\) are ordinary members of the same basis.
The Grand Meson lift is
\[
  \Gamma_{\mathrm{GM}}(O_{q\bar r})
  :=
  (i,j,O_{q\bar r})
  \quad
  \text{where }q\in A_i,\ r\in A_j.
\]
Thus
\[
  \mathsf M_{\mathrm{GM}}
  :=
  \{\,(i,j,O_{q\bar r})\mid q\in A_i,\ r\in A_j,\ 1\le i,j\le3\,\}.
\]

\begin{proposition}[Conservative operator-basis lift]
Let
\[
  \pi_{\mathrm{QCD}}(i,j,O_{q\bar r})=O_{q\bar r}.
\]
Then
\[
  \pi_{\mathrm{QCD}}\circ\Gamma_{\mathrm{GM}}
  =
  \mathrm{id}_{\mathsf Q_{\mathrm{mes}}}.
\]
Therefore the Grand Meson is a conservative lift of the QCD mesonic
operator basis: it adds the three-axis pair label \((i,j)\) while
preserving the color-singlet QCD operator.
\end{proposition}

\begin{remark}[Selector-relative completion property]
Relative to a closed package selector \(\widehat P\), the object
\(\mathsf{GM}_{36}\) is used here as a selector-relative conservative
channel-index lift of \(\mathsf Q_{\mathrm{mes}}\) satisfying the following
conditions:
\begin{enumerate}[label=(\roman*)]
  \item each \(O_{q\bar r}\) has the unique generation-axis pair
    \((i,j)\) determined by \(q\in A_i\) and \(r\in A_j\);
  \item forgetting the axis pair and package data recovers \(O_{q\bar r}\);
  \item anti-face replacement and top-bearing ordinary readout produce
    the typed contradiction witnesses \(\Contr_{\bar F}\) and
    \(\Contr_{\mathrm{top}}(-;\mathcal R_{\mathrm{ch}})\) unless their
    residual channels close;
  \item no new color representation or color force is introduced;
  \item the QCD quantum numbers, source Lagrangian, correlators, and CKM
    charged-current layer are preserved under forgetting.
\end{enumerate}
This is a selector-relative labeling and closure property, not a category-theoretic
universal property in an unintroduced category.  If a later version defines
such a category of completions, the required comparison map would have the
form
\[
  \theta:\mathsf{GM}_{36}\longrightarrow\mathcal X
\]
for a completion \(\mathcal X\) equipped with its own recovery map
\(\pi_{\mathcal X}:\mathcal X\to\mathsf Q_{\mathrm{mes}}\), with
\[
  \mathsf{GM}_{36}^{\mathrm{ch,cl}}
  :=
  \{\,(i,j,P_{q\bar r})\in\mathsf{GM}_{36}^{\mathrm{ch}}
  \mid P_{q\bar r}\in\mathsf{Pol}^{\mathrm{res}}_{q\bar r}\,\}
\]
and a single dependent injection
\[
  \iota^{36}:\mathsf{GM}_{36}^{\mathrm{ch,cl}}\to\mathsf{GM}_{36},
  \qquad
  \iota^{36}(i,j,P_{q\bar r})
  :=
  G^{(q\bar r,P)},
\]
where all \(36\) slots are initialized by
\[
  G^{(q\bar r,P)}(a,\bar b)
  :=
  \begin{cases}
    P, & (a,\bar b)=(q,\bar r),\\
    \mathbf 0_{a\bar b}[\mathrm{buried}], & \text{otherwise}.
  \end{cases}
\]
Choose a closed package selector
\[
  \widehat P:\mathsf Q_{\mathrm{mes}}\to\mathsf{Pol}^{\mathrm{res}},
  \qquad
  \widehat P(O_{q\bar r})\in\mathsf{Pol}^{\mathrm{res}}_{q\bar r}.
\]
For top-bearing operators, \(\widehat P\) selects only a weak-virtual closed
package or a closed inactive residual package; it never selects an ordinary
top-meson readout package.
Then define
\[
  \widehat{\Gamma}^{\widehat P}_{\mathrm{GM}}(O_{q\bar r})
  :=
  (i,j,\widehat P(O_{q\bar r})),
  \qquad q\in A_i,\ r\in A_j.
\]
Thus
\[
  \pi_{\mathcal X}\circ\theta\circ
  \iota^{36}\circ\widehat{\Gamma}^{\widehat P}_{\mathrm{GM}}
  =
  \mathrm{id}_{\mathsf Q_{\mathrm{mes}}}.
\]
\end{remark}

\begin{definition}[Grand Meson source Lagrangian]
Write the quark-sector QCD Lagrangian as
\[
  \mathcal L_{\mathrm{QCD}}
  =
  -\frac14G^A_{\mu\nu}G^{A\mu\nu}
  +
  \sum_{q\in F_6}\bar q(i\gamma^\mu D_\mu-m_q)q .
\]
The Grand Meson source lift is
\[
  \mathcal L_{\mathrm{GM}}[J]
  :=
  \mathcal L_{\mathrm{QCD}}
  +
  \sum_{i,j=1}^{3}
  \sum_{\substack{q\in A_i\\ r\in A_j}}
  \sum_{\sigma}
  \left(
    J_{ij,\sigma}^{q\bar r}\,O^{\Gamma_\sigma}_{q\bar r}
    +
    \overline{J_{ij,\sigma}^{q\bar r}}\,
    (O^{\Gamma_\sigma}_{q\bar r})^\dagger
  \right).
\]
Here \(J_{ij,\sigma}^{q\bar r}\) is not a new color force.  It is the
closed Grand Meson source attached to the axis pair \((i,j)\) and
spin-parity sector \(\sigma\).  The Hermitian-conjugate term is included
so that charged or otherwise non-Hermitian bilinears give a real
Lagrangian density.
\end{definition}

\begin{proposition}[Lagrangian recovery]
Setting all Grand Meson sources to zero recovers QCD:
\[
  \mathcal L_{\mathrm{GM}}[0]=\mathcal L_{\mathrm{QCD}}.
\]
Forgetting the axis-pair labels sends the lifted source terms back to the
ordinary mesonic source sector
\[
  J_{\sigma}^{q\bar r}:=J_{ij,\sigma}^{q\bar r}
  \quad(q\in A_i,\ r\in A_j),
  \qquad
  \sum_{q,r\in F_6}\sum_{\sigma}
  J_{\sigma}^{q\bar r}O^{\Gamma_\sigma}_{q\bar r}.
\]
Thus the Grand Meson completes the mesonic Lagrangian source layer by
adding axis-channel closure, not by altering the color-gauge core.
\end{proposition}

\begin{definition}[Grand Meson quantum numbers]
Recall the previously defined QCD quantum fingerprint
\(\nu_{\mathrm{QCD}}(q,\bar r;\sigma)\).
The Grand Meson lift is
\[
  \nu_{\mathrm{GM}}(q,\bar r;\sigma)
  :=
  (i,j,\nu_{\mathrm{QCD}}(q,\bar r;\sigma)),
  \qquad q\in A_i,\ r\in A_j .
\]
Here \(\sigma\) may be \(J^{PC}\) for neutral channels; for charged or
open-flavor channels it is the corresponding spin-parity sector without an
unavailable charge-conjugation label.
\end{definition}

\begin{proposition}[Quantum-number recovery]
If \(\pi_\nu(i,j,\nu)=\nu\), then
\[
  \pi_\nu\circ\nu_{\mathrm{GM}}
  =
  \nu_{\mathrm{QCD}}.
\]
Thus the Grand Meson completes mesonic quantum numbers by adding only
the axis-pair quantum number \((i,j)\), while preserving charge, flavor,
baryon number, color singletness, and the spin-parity sector.
\end{proposition}

\begin{definition}[Grand Meson observables]
For QCD mesonic operators \(O^{\Gamma_\sigma}_{q\bar r}\), write the
ordinary two-point observable as
\[
  C^{\sigma\tau}_{q\bar r,s\bar t}(x-y)
  :=
  \left\langle
  O^{\Gamma_\sigma}_{q\bar r}(x)
  \bigl(O^{\Gamma_\tau}_{s\bar t}(y)\bigr)^{\dagger}
  \right\rangle .
\]
The Grand Meson lift is the axis-closed observable
\[
  C^{\mathrm{GM},\sigma\tau}_{ij,kl}(q\bar r,s\bar t;x-y)
  :=
  (i,j,k,l,\ C^{\sigma\tau}_{q\bar r,s\bar t}(x-y)),
\]
where \(q\in A_i,\ r\in A_j,\ s\in A_k,\ t\in A_l\).
\end{definition}

\begin{proposition}[Observable recovery]
Let \(\pi_{\mathrm{obs}}(i,j,k,l,C)=C\).  Then
\[
  \pi_{\mathrm{obs}}
  \bigl(C^{\mathrm{GM},\sigma\tau}_{ij,kl}(q\bar r,s\bar t;x-y)\bigr)
  =
  C^{\sigma\tau}_{q\bar r,s\bar t}(x-y).
\]
Thus masses, widths, and spectral poles read from ordinary QCD correlators
are preserved, while the Grand Meson retains which axis-pair channel made
the observable readable.
\end{proposition}

\begin{definition}[Grand Meson conservation law]
Let \(\mathbf a_{ij}\) be the unit basis element of
\(\mathbb Z^{3\times3}\).  For \(q\in A_i\) and \(r\in A_j\), define
\[
  K_{\mathrm{QCD}}(q\bar r)
  :=
  (Q_q-Q_r,\ e_q-e_r,\ \mathsf B_{\mathrm{ary}}=0,\
  \mathbf 1_{\mathrm c})
\]
and lift it to
\[
  K_{\mathrm{GM}}(q\bar r)
  :=
  (\mathbf a_{ij},\ K_{\mathrm{QCD}}(q\bar r)).
\]
Let \(\mathcal R_{\mathrm{axis}}\subseteq\mathbb Z^{3\times3}\) be the
declared set of closed axis-residue records, and define
\[
  \AxisCl(R)
  \quad\Longleftrightarrow\quad
  R\in\mathcal R_{\mathrm{axis}}.
\]
\end{definition}

\begin{proposition}[Conservation-law recovery]
For an oriented mesonic process
\(\mathcal P=\sum_{\alpha}\eta_{\alpha}(q_\alpha\bar r_\alpha)\), ordinary
QCD conservation is
\[
  \sum_{\alpha}\eta_{\alpha}
  K_{\mathrm{QCD}}(q_\alpha\bar r_\alpha)=0 .
\]
The Grand Meson conservation condition is
\[
  R_{\mathrm{axis}}(\mathcal P)
  :=
  \sum_{\alpha}\eta_{\alpha}\mathbf a_{i_\alpha j_\alpha},
  \qquad
  \sum_{\alpha}\eta_{\alpha}
  K_{\mathrm{GM}}(q_\alpha\bar r_\alpha)
  =
  (R_{\mathrm{axis}}(\mathcal P),0).
\]
Thus QCD conservation is recovered by forgetting the axis residue
\(R_{\mathrm{axis}}\).  A closed Grand Meson process has
\(R_{\mathrm{axis}}=0\); otherwise the nonzero axis residue must satisfy
\[
  \AxisCl(R_{\mathrm{axis}}(\mathcal P))
\]
rather than being ignored.
\end{proposition}

At this bookkeeping level, the mesonic flavor sector of QCD is represented
compactly as the union of one-axis terms \((i=i)\) and two-axis terms
\((i\ne j)\) among the three Grand Meson axes.  The dynamics of color is not discarded; it is the
singlet contraction already present in \(O_{q\bar r}\).  Channels touching
\(\qt\) are retained as weak-virtual channels satisfying closure, not as ordinary
top mesons.

\section{Lorentz-Covariant Readout Condition}

The Grand Meson must also avoid the classical aether failure.  It is not a
hidden medium with an absolute state of rest.  It is a local six-face
mediator with a \(36\)-channel oriented body whose outputs must be readable
without introducing an absolute frame.
The nickname sometimes used for this condition is not a claim of Einstein's
endorsement.  It is only a shorthand for the Lorentz-covariant readout
condition: no mesonic channel calculus may reintroduce an absolute hidden
medium.

\begin{axiom}[Lorentz-covariant readout: no absolute mesonic frame]
No equation in the Grand Meson theory may depend on a privileged global
rest frame of the mediator.  Only resolved flavor channels, local channel closure, and
observer-readable projections may be used.
For a Lorentz transformation \(\Lambda\), the flavor-axis labels
\((i,j)\) are internal labels and remain fixed, while spacetime arguments
and tensor indices transform in the ordinary way:
\[
  (i,j,O^{\Gamma_\sigma}_{q\bar r}(x))
  \longmapsto
  (i,j,O^{\prime\,\Gamma'_\sigma}_{q\bar r}(\Lambda x)).
\]
Observable statements must therefore be Lorentz scalars or covariant tensor
statements after forgetting the internal Grand Meson labels.
The source layer must satisfy
\[
  \mathcal L_{\mathrm{GM}}[J](x)
  \longmapsto
  \mathcal L'_{\mathrm{GM}}[J'](\Lambda x)
  =
  \mathcal L_{\mathrm{GM}}[J](x),
\]
and the lifted correlator must transform only through its spacetime
arguments and tensor indices:
\[
  C^{\mathrm{GM},\sigma\tau}_{ij,kl}(x-y)
  \longmapsto
  C_{\mathrm{GM}}^{\prime\,ij,kl,\sigma'\tau'}(\Lambda(x-y)).
\]
Thus \((i,j)\) are internal scalar labels, not aether-like spacetime
degrees of freedom.
\end{axiom}

This axiom does not ban mediation.  It bans absolute mediation.  The Grand
Meson is therefore not a return to the classical aether.  It is a
channel-resolved local mediator that must survive projection into closed
observations.

\section{Minimal Cover Relative to the Fixed Six-Flavor Input}

Formally one may define an \(n\)-meson by
\[
  G_n:=\{1,\ldots,n\},
  \qquad
  F_{2n}:=G_n\times H_2 .
\]
For a formal flavor set \(S\), assume a typed pre-package family
\[
  \mathsf{PrePol}^{S,\mathrm{res}}_{a\bar b}
  \qquad(a,b\in S),
\]
and define the corresponding relative face by
\[
  \mathsf{Face}^{S,\mathrm{res}}_{a|S}
  :=
  \prod_{b\in S}\mathsf{PrePol}^{S,\mathrm{res}}_{a\bar b}
  \times
  \prod_{c\in S}\mathsf{PrePol}^{S,\mathrm{res}}_{c\bar a}.
\]
Then
\[
  \mathsf{Mes}_n
  :=
  \prod_{(i,\epsilon)\in F_{2n}}
  \mathsf{Face}^{F_{2n},\mathrm{res}}_{(i,\epsilon)|F_{2n}} .
\]
The case \(n=1\) is the formal two-face analog of the General Meson; it
becomes the General Meson after choosing the identification
\(F_2\cong A_Y\).  The case \(n=3\) becomes the Grand Meson after applying
the observed-flavor identification \(\Phi:F_6\cong G_3\times H_2\).

The reason to stop at \(n=3\) is not that higher \(n\) is impossible, and
it is not a proof of why nature has exactly three generations.  It is that
the known six-flavor quark sector already factors as
\[
  F_6\cong G_3\times H_2 .
\]
Therefore \(n=3\) is the exact internal-generation cover of the present
mesonic flavor sector:
\[
  \mathsf{Mes}_3
  \cong
  \prod_{(i,\epsilon)\in G_3\times H_2}
  \mathsf{Face}^{\mathrm{res}}_{\Phi(i,\epsilon)|F_6}.
\]
For \(n>3\), additional axes require additional readout structure.  Such
structure may be meaningful in a later theory, but it is not required for
the present six-flavor sector.  No order relation on readout power is used
here; the claim is only minimality relative to the fixed six-flavor input.

Thus \(n=3\) is the minimal complete cover for the present Grand Meson
input: complete because it covers the known three-generation quark sector,
minimal because no fourth axis is introduced without a corresponding
standard-model flavor input.  This is not a theorem explaining why nature
has three generations.  It is the closure statement for the currently used
six-flavor quark input; if the input sector changes, the update procedure
must be rerun rather than silently extended.

\section{Closed Transition}

Grand Meson robustness is not the absence of change.  It is the closure of
every changed face or body channel.  The body version was defined in the
Grand Fuse section.  The face version is as follows.  Let a proposed face
transition symbol be written
\[
  u:g\to g'.
\]
It carries source and target skeletons
\[
  s(u)=g,\qquad t(u)=g'.
\]
Define its changed-face support by
\[
  \Delta_{\mathrm{face}}(u)
  :=
  \{q\in F_6\mid s(u)(q)\ne t(u)(q)\}.
\]

\begin{definition}[Grand Meson transition space]
The face transition space is
\[
  \Mor^{\mathrm{face}}_{\mathrm{GM}}
  :=
  \{\,u:g\to g'
  \mid
  \Delta_{\mathrm{face}}(u)\subseteq\RCl_{\mathrm{face}}(u)\,\}.
\]
The contradiction predicate for a proposed transition symbol is
\[
  \Contr_{\mathrm{tr}}(u)
  :=
  \Delta_{\mathrm{face}}(u)\setminus\RCl_{\mathrm{face}}(u)
  \ne\varnothing .
\]
\end{definition}

\begin{proposition}[Transition block]
If \(\Contr_{\mathrm{tr}}(u)\), then
\[
  u\notin\Mor^{\mathrm{face}}_{\mathrm{GM}}.
\]
Consequently a channel-boundary crossing without closure does not name an
operation inside the Grand Meson theory; it is a contradiction witness
outside the transition space.
\end{proposition}

\begin{proof}
By definition, \(u\in\Mor^{\mathrm{face}}_{\mathrm{GM}}\) requires
\(\Delta_{\mathrm{face}}(u)\subseteq\RCl_{\mathrm{face}}(u)\).  The
predicate \(\Contr_{\mathrm{tr}}(u)\) states that
\(\Delta_{\mathrm{face}}(u)\setminus\RCl_{\mathrm{face}}(u)\) is nonempty.
These conditions are inconsistent, so the proposed symbol cannot inhabit
\(\Mor^{\mathrm{face}}_{\mathrm{GM}}\).
\end{proof}

\begin{definition}[Physical well-formedness]
A physically well-formed Grand Meson transition must satisfy
\[
  \mathrm{Cons}_{\mathrm{QCD}}(u)
  \Longleftrightarrow
  \text{the QCD conservation vector of the transition carried by }u
  \text{ is zero},
\]
\[
  \mathrm{Lag}_{\mathrm{GM}}(u)
  \Longleftrightarrow
  \text{the transition carried by }u
  \text{ has a declared Grand Meson source-layer term},
\]
and
\[
  \mathrm{Obs}_{\mathrm{GM}}(u)
  \Longleftrightarrow
  \text{the transition carried by }u
  \text{ has a declared observable readout or correlator}.
\]
Then
\[
  \mathrm{PhysWF}(u)
  :=
  \bigl(u\in\Mor^{\mathrm{face}}_{\mathrm{GM}}\bigr)
  \wedge
  \mathrm{Cons}_{\mathrm{QCD}}(u)
  \wedge
  \mathrm{Lag}_{\mathrm{GM}}(u)
  \wedge
  \mathrm{Obs}_{\mathrm{GM}}(u).
\]
Here \(\mathrm{Cons}_{\mathrm{QCD}}\) means that the conservation condition
closes, \(\mathrm{Lag}_{\mathrm{GM}}\) means that the transition has a
defined Lagrangian-source layer, and \(\mathrm{Obs}_{\mathrm{GM}}\) means
that an observable readout exists.
\end{definition}

Equivalently,
\[
  \text{non-transition}=\text{unclosed discontinuity}.
\]
The discontinuity itself is not the contradiction.  Without channel closure,
the corresponding transition symbol has no place in the typed Grand Meson
transition spaces.

\section{Conclusion}

The Grand Meson is not proposed as an omnipotent meson.  It is proposed as
a closed \(n=3\) channel-completion calculus for mesonic sectors:
\[
  \mathsf{Grand}=\mathsf{Grand}_{\mathrm{comp}}
  =
  \operatorname{Im}
  \bigl(\skel:\mathsf{Body}_{36}^{\mathrm{cl}}
  \to\mathsf{Grand}^{\mathrm{raw}}\bigr),
  \qquad
  \mathsf{GM}_{36}=\mathsf{Body}_{36}^{\mathrm{cl}}.
\]
It conservatively recovers the General Meson by a surjective projection,
replaces missing channels with resolved flavor channels, avoids an absolute aether frame,
and treats robustness as channel closure rather than immobility.  Its backward
compatibility is therefore responsible: extra axes may be fused into the
older face only with residual closure, while unclosed fission reduces to a
typed Grand Meson contradiction and has an empty transition class.

The path is therefore narrow.  Begin with the \(\qu\leftrightarrow\qd\)
eye that already works.  Open \(\qc\leftrightarrow\qs\) and
\(\qt\leftrightarrow\qb\) without breaking it.  Stop at \(n=3\) until a
future theory can make higher axes readable without turning them into a
burden of infinite explanation.

\section*{Non-Technical Appendix: Observer-Side Fission}

This note is not used in any theorem above.  It records a philosophical
reading of the downgrade discipline.  Let a concept or entity \(X\) be
represented by a closed Grand Meson state \(g_X\).  A thought experiment may
introduce a proposed fission symbol \(d:g_X\Downarrow m_X\) and later
reclose the discussion by fusion.  This does not damage the technical
calculus when the whole argument remains inside the typed transition
spaces.  If, however, the proposed fission leaves a contradiction witness
\[
  \Contr_{\mathrm{dow}}(d),
\]
then the symbol has already left the Grand Meson transition space.  As an
observer-side convention, a later observer class \(\mathcal O\) may record
a closed reading and a fission-intent reading,
\[
  r_{\mathrm{closed}},r_{\mathrm{intent}}\in\Read_{\mathcal O}(X),
  \qquad
  r_{\mathrm{closed}}\ne r_{\mathrm{intent}}.
\]
This is an interpretive appendix, not a consequence of Lorentz covariance
or of the Lorentz-covariant readout condition.

\section*{Acknowledgement}

The author acknowledges Hideki Yukawa, whose meson theory supplies the
foundational mediator problem from which this construction begins.  The
author also acknowledges Albert Einstein, whose relativistic limit on
classical mediation clarifies the boundary region exposed by the theoretical
dialogue with Yukawa's mesonic idea.  Finally, the author thanks OpenAI and
GPT-5.5 for helping weave this idea into a coherent manuscript and for
respecting the strict confidentiality required during the drafting process.

\begin{thebibliography}{9}

\bibitem{Yukawa1935}
H. Yukawa.
On the interaction of elementary particles.
\emph{Proceedings of the Physico-Mathematical Society of Japan},
17:48--57, 1935.

\bibitem{Einstein1905}
A. Einstein.
On the electrodynamics of moving bodies.
\emph{Annalen der Physik}, 17:891--921, 1905.

\end{thebibliography}

\end{document}
